---
title: "FactorAnalysis RMarkdown"
author: "Alexandra Lautarescu"
date: "29/01/2021"
output:
  pdf_document: 
    toc: true 
    toc_depth: 4
---

# SETTING UP THE R ENVIRONMENT

Disabling scientific notation
```{r}
options(scipen=999)
```

Loading necessary packages (supressing messages from appearing in RMarkdown output)
```{r message = FALSE}
library(Hmisc)
library(plyr)
library(psych)
library(nFactors)
library(GPArotation)
library(lavaan)
library(dplyr)
library(janitor)
library(ggplot2)
library(rcompanion)
library(cowplot)
library(harrypotter)
library(pastecs)
library(tidyr)
library(reshape2)
library(effsize)
library(MBESS)
library(semTools)
library(knitr)
library(semPlot)
library(equaltestMI)
```

Qualtrics data refers to the high risk prenatal sample. 
dHCP prenatal / fetal / antenatal - refers to the community prenatal sample
dHCP postnatal / neonatal - refers to the community postnatal sample 

# QUALTRICS DATA  

Loading dataframe for qualtrics data 
```{r}
data_qualtrics <-read.csv("data_qualtrics.csv", header=TRUE, na.strings=c("","NA", " ", "not known"))
```

## Initial descriptives & Data prep - Qualtrics data 

Describing dataframe. Hiding results from RMarkdown (as it would take up too much space)
```{r results=FALSE}
describe(data_qualtrics) 
```

Changing type for one variable
```{r}
data_qualtrics$partticipantID <-as.character(data_qualtrics$partticipantID)
```

**Creating a dataframe with categorical variables for descriptive purposes only**
```{r}
data_qualtrics2 <- data_qualtrics
data_qualtrics2$EPDS_1 <- factor(data_qualtrics2$EPDS_1, levels=c(0,1,2,3),
                                labels=c("As much as..", "Not quite", "Definitely not", "Not at all"))

data_qualtrics2$EPDS_2 <- factor(data_qualtrics2$EPDS_2, levels=c(0,1,2,3),
                                labels=c("As much as..", "Rather less", "Definitely less", "Hardly"))

data_qualtrics2$EPDS_3 <- factor(data_qualtrics2$EPDS_3, levels=c(0,1,2,3),
                                labels=c("Never", "Not often", "Sometimes", "Yes, most")) 

data_qualtrics2$EPDS_4 <- factor(data_qualtrics2$EPDS_4, levels=c(0,1,2,3),
                                labels=c("No", "Hardly", "Sometimes", "Yes"))                   

data_qualtrics2$EPDS_5 <- factor(data_qualtrics2$EPDS_5, levels=c(0,1,2,3),
                                labels=c("Not at all", "Not much", "Sometimes", "Yes"))   

data_qualtrics2$EPDS_6 <- factor(data_qualtrics2$EPDS_6, levels=c(0,1,2,3),
                                labels=c("No", "No, most time..", "Sometimes", "Yes"))   

data_qualtrics2$EPDS_7 <- factor(data_qualtrics2$EPDS_7, levels=c(0,1,2,3),
                                labels=c("No", "Not very", "Sometimes", "Yes"))

data_qualtrics2$EPDS_8 <- factor(data_qualtrics2$EPDS_8, levels=c(0,1,2,3),
                                labels=c("No", "Not very", "Often", "Yes"))

data_qualtrics2$EPDS_9 <- factor(data_qualtrics2$EPDS_9, levels=c(0,1,2,3),
                                labels=c("No", "Occasionally", "Often", "Yes"))

data_qualtrics2$EPDS_10 <- factor(data_qualtrics2$EPDS_10, levels=c(0,1,2,3),
                                 labels=c("Never", "Hardly", "Sometimes", "Yes"))
```

Checking structure of new dataframe.
```{r results=FALSE}
str(data_qualtrics2) 
```

Calculating % for frequency of response for each answer (manually just to be sure)
```{r}
summary(data_qualtrics2$EPDS_1)
```
Calculating percentages 
7100/266 = 26.69 %  
13400/266 = 50.37 %  
5600/266 = 21.05 %  
500/266 = 1.87  %  

```{r}
summary(data_qualtrics2$EPDS_2)
```

4500/266 = 16.91  %  
11900/266 = 44.73 %  
8000/266 = 30.07 %  
2200/266 = 8.27 %  

```{r}
summary(data_qualtrics2$EPDS_3)
```

1200/266 = 4.51 %  
5500/266 = 20.67 %  
12300/266 = 46.24 %  
7600/266 = 28.57 %  

```{r}
summary(data_qualtrics2$EPDS_4)
```
800/266 = 3.00 %  
2000/266 = 7.51 %  
12800/266 = 48.12  %  
11000/266 = 41.35 %  

```{r}
summary(data_qualtrics2$EPDS_5)
```

2000/266 = 7.51 %  
5500/266 = 20.67 %  
12300/266 = 46.24 %  
6800/266 = 25.56 %  

```{r}
summary(data_qualtrics2$EPDS_6)
```

1100/266 = 4.13 %  
4200/266 = 15.78 %  
17200/266 = 64.66 %  
4100/266 = 15.41 %  

```{r}
summary(data_qualtrics2$EPDS_7)
```

4400/266 = 16.54 %  
7600/266 = 28.57 %  
10200/266 = 38.34 %  
4400/266 = 16.54 %  

```{r}
summary(data_qualtrics2$EPDS_8)
```
1500/266=5.63 %  
7400/266=27.81 %  
13400/266=50.37 %  
4300/266=16.16 %  

```{r}
summary(data_qualtrics2$EPDS_9)
```

4500/266 = 16.91 %  
10600/266 = 39.84 %  
8600/266 = 32.33 %  
2900/266 = 10.90 %  

```{r}
summary(data_qualtrics2$EPDS_10)
```

17600/266 = 66.16 %  
5200/266 = 19.54 %  
3500/266 = 13.15 %  
300/266 = 1.12 %  

To double-check that these numbers are correct, also doing this. All seems fine.
Results hidden to save space 
```{r results="hide", warning=FALSE, comment=FALSE, message=FALSE}
((plyr::count(data_qualtrics$EPDS_1))*100)/266
((plyr::count(data_qualtrics$EPDS_2))*100)/266
((plyr::count(data_qualtrics$EPDS_3))*100)/266
((plyr::count(data_qualtrics$EPDS_4))*100)/266
((plyr::count(data_qualtrics$EPDS_5))*100)/266
((plyr::count(data_qualtrics$EPDS_6))*100)/266
((plyr::count(data_qualtrics$EPDS_7))*100)/266
((plyr::count(data_qualtrics$EPDS_8))*100)/266
((plyr::count(data_qualtrics$EPDS_9))*100)/266
((plyr::count(data_qualtrics$EPDS_10))*100)/266
```

**Going back to the main database with integers instead of categories from now on**

Calculating the sum of cases who scored 11 or more on the EPDS 
```{r}
sum(data_qualtrics$EPDS_Total>10, na.rm=TRUE)
```

Calculating the sum of cases who scored 13 or more on the EPDS 
```{r}
sum(data_qualtrics$EPDS_Total>12, na.rm=TRUE)
```


## FACTOR ANALYSIS (Qualtrics sample)
Creating subset of dataframe with only the variables needed for EFA. 
Then checking the structure to make sure it's alright. Results hidden to save space. 
```{r results='hide'}
data_qualtrics_FA <- subset(data_qualtrics, select=c(-partticipantID, -EPDS_Total, 
                                                     -GAatScreen, -MatAgeAtScreen))
str(data_qualtrics_FA)
```

Calculating Cronbach's alpha (hid results as outputs includes alpha for each individual question too)
```{r results ='hide'}
psych::alpha(data_qualtrics_FA)
```

Calculating McDonald's omega 
```{r results ='hide'}
ci.reliability(data_qualtrics_FA, type="omega")
```


Creating subset of FA database without the 10th question
```{r results='hide'}
data_qualtrics_FA_Less10 <- subset(data_qualtrics_FA, select=c(-EPDS_10))
str(data_qualtrics_FA_Less10)
```

Need to create 2 subsets - one for EFA (40%) and one for CFA (60%)
```{r results='hide'}
set.seed(1)
n=nrow(data_qualtrics)
data_qualtrics_Index = sample(1:n, size=round(0.6*n), replace=FALSE)
data_qualtrics_CFA60 = data_qualtrics_FA [data_qualtrics_Index ,]
data_qualtrics_EFA40 = data_qualtrics_FA [-data_qualtrics_Index ,]
str(data_qualtrics_CFA60)
str(data_qualtrics_EFA40)
```

### EFA with Pearson correlation matrix (Qualtrics data)
Calculating a correlation matrix and saving it 
```{r}
data_qualtrics_EFA40_Matrix <- cor(data_qualtrics_EFA40)
```

Displaying the correlation matrix using 2 decimal places. Checking if there are any above 9,
to avoid multicollinearity (there are not) or any that do not correlate at all with other 
(there are not). 
```{r}
round(data_qualtrics_EFA40_Matrix,2)
```

Doing Kaiser-Mayer-Olkin (KMO) measure of sampling adequacy.KMO measures of sampling 
adequacy were >.79, well above the acceptable limit of .5.
```{r}
KMO(data_qualtrics_EFA40_Matrix)
```

Doing Bartlett's test of sphrericity.Bartlett’s test of sphericity p<.05 indicated that the 
correlations between items were sufficiently large for factor analysis
```{r}
cortest.bartlett(data_qualtrics_EFA40_Matrix,106)
```

Calculating the determinant of the correlation matrix.  The determinant of the correlation matrix
was greater than the necessary value of .00001. 
```{r}
det(data_qualtrics_EFA40_Matrix)
```

 Get eigenvalues 
```{r}
ev_data_qualtrics_EFA40<- eigen(cor(data_qualtrics_EFA40)) 
ev_data_qualtrics_EFA40
```

Get scree plot .
```{r}
scree_data_qualtrics_EFA40  <- scree(data_qualtrics_EFA40)
scree_data_qualtrics_EFA40
```

Doing Parallel analysis 
Parallel analysis using fa.parallel 
```{r}
parallel_data_qualtrics_EFA40<- fa.parallel(data_qualtrics_EFA40_Matrix, n.obs=106, 
                                            main="Parallel Analysis Scree Plots",fa="fa",
                                            fm="mrfa", SMC=TRUE, quant=.95, n.iter=500)
parallel_data_qualtrics_EFA40
```

Doing the exploratory factor analysis now 
```{r }
data_qualtrics_EFA40_Analysis1<-factanal(data_qualtrics_EFA40,2, 
                                         rotation="oblimin", fm="mle")
print(data_qualtrics_EFA40_Analysis1, digits=2, cutoff=.30, sort=FALSE)
```

```{r}
data_qualtrics_EFA40_Analysis2<-factanal (data_qualtrics_EFA40,3, rotation="oblimin", 
                                          fm="mrfa")
print(data_qualtrics_EFA40_Analysis2, digits=2, cutoff=.30, sort=FALSE)
```

### EFA with Polychoric correlation matrix (Qualtrics data)

Doing the above again, with a polychoric correlation matrix this time (as per Lysdottir et al.).
The default version adds .5 correction for continuity by default. However, corrections for continuity are not advised when categorical variables have more than 2 categories. Thus, we used correct=FALSE. 

```{r}
a <- psych::polychoric(data_qualtrics_EFA40, correct=FALSE) 
data_qualtrics_EFA40_PolychorMatrix <- a$rho
``` 


Displaying the correlation matrix using 2 decimal places.Checking if there are any above 9, to avoid multicollinearity (there are not) or any that don't correlate at all with other (there are not). 
```{r}
round(data_qualtrics_EFA40_PolychorMatrix,2)
```

Doing Kaiser-Mayer-Olkin (KMO) measure of sampling adequacy.
KMO measures of sampling adequacy well above the acceptable limit of .5.  
```{r}
KMO(data_qualtrics_EFA40_PolychorMatrix)
```

Doing Bartlett's test of sphrericity (indicated that the correlations between items were sufficiently large for factor analysis)
```{r}
cortest.bartlett(data_qualtrics_EFA40_PolychorMatrix,106)
```

Calculating the determinant of the correlation matrix. The determinant of the correlation matrix was greater than the necessary value of .00001. 
```{r}
det(data_qualtrics_EFA40_PolychorMatrix)
```

 
Get eigenvalues and scree plot. Checking the tail end of eigenvalues to make sure all are non-negative All are >0 , which means that we have obtained a proper correlation matrix. Check eigenvalues >1
```{r}
ev_data_qualtrics_EFA40_Polychor<- eigen(data_qualtrics_EFA40_PolychorMatrix)
ev_data_qualtrics_EFA40_Polychor
```

```{r}
scree_data_qualtrics_EFA40_Polychor  <- scree(data_qualtrics_EFA40_PolychorMatrix)
scree_data_qualtrics_EFA40_Polychor 
```

```{r}
parallel_data_qualtrics_EFA40_Polychoric<- fa.parallel(data_qualtrics_EFA40_Matrix, n.obs=106, 
                                                       main="Parallel Analysis Scree Plots",
                                                       fa="fa", fm="mrfa",
                                                       cor="poly", quant=.95, SMC=TRUE,
                                                       n.iter=500)
parallel_data_qualtrics_EFA40_Polychoric
```

Doing the exploratory factor analysis now 
```{r}
data_qualtrics_EFA40_Polychor_Analysis1<-factanal (covmat=data_qualtrics_EFA40_PolychorMatrix,
                                                   factors=2, 
                                                   rotation="oblimin", fm="mle")
print(data_qualtrics_EFA40_Polychor_Analysis1, digits=2, cutoff=.30, sort=FALSE)
```

```{r}
data_qualtrics_EFA40_Polychor_Analysis2<-factanal(covmat=data_qualtrics_EFA40_PolychorMatrix,
                                                  factors=3, 
                                                  rotation="oblimin", fm="mle")
print(data_qualtrics_EFA40_Polychor_Analysis2, digits=2, cutoff=.30, sort=FALSE)
```

### CFA (Qualtrics data )

Now, doing the confirmatory factor analysis. Hiding results as otherwise document would be very long 

#### From EFA - 3 FACTOR MODEL
```{r}
data_qualtrics_CFA_Model_3f <- ' depression  =~ EPDS_7 + EPDS_8 + EPDS_9 + EPDS_10     
              anhedonia =~ EPDS_1 + EPDS_2 
              anxiety  =~ EPDS_3 + EPDS_4 + EPDS_5 '
```

Fitting the model with WLSMV:
```{r}
data_qualtrics_CFA_Model_3f_fitW <- cfa(data_qualtrics_CFA_Model_3f, 
                                        data=data_qualtrics_CFA60,estimator="WLSMV", 
                                        ordered=c("EPDS_1", "EPDS_2","EPDS_3","EPDS_4","EPDS_5",
                                                  "EPDS_7","EPDS_8","EPDS_9","EPDS_10"))
```

```{r results='hide'}
summary(data_qualtrics_CFA_Model_3f_fitW, standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
data_qualtrics_CFA_Model_3f_fitM <- cfa(data_qualtrics_CFA_Model_3f, data=data_qualtrics_CFA60)
```

```{r results='hide'}
summary(data_qualtrics_CFA_Model_3f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### From EFA - 2 FACTOR MODEL 
```{r}
data_qualtrics_CFA_Model_2f <- 'anhedonia =~ EPDS_1 + EPDS_2 
                                depression =~ EPDS_3 + EPDS_5 + EPDS_6 + EPDS_7 + EPDS_8 +
                                              EPDS_9 + EPDS_10'
```

Fitting the model with WLSMV:
```{r results='hide'}
data_qualtrics_CFA_Model_2f_fitW <- cfa(data_qualtrics_CFA_Model_2f, 
                                        data=data_qualtrics_CFA60,estimator="WLSMV",
                                        ordered=c("EPDS_1", "EPDS_2","EPDS_3","EPDS_4","EPDS_5",
                                                  "EPDS_6","EPDS_7","EPDS_8","EPDS_9","EPDS_10"))

summary(data_qualtrics_CFA_Model_2f_fitW, standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r results='hide'}
data_qualtrics_CFA_Model_2f_fitM <- cfa(data_qualtrics_CFA_Model_2f, data=data_qualtrics_CFA60)

summary(data_qualtrics_CFA_Model_2f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### ZHONG MODEL
```{r}
data_qualtrics_CFA_ZHONG_Model <- 'anhedonia =~ EPDS_1 + EPDS_2 
            depression  =~ EPDS_3 + EPDS_4 + EPDS_5 + EPDS_6 + EPDS_7 + EPDS_8 + EPDS_9 + EPDS_10'     
```
Fitting the model with WLSMV:
```{r results='hide'}
data_qualtrics_CFA_ZHONG_Model_fitW <- cfa(data_qualtrics_CFA_ZHONG_Model, 
                                           data=data_qualtrics_CFA60,estimator="WLSMV", 
                                           ordered=c("EPDS_1", "EPDS_2","EPDS_3","EPDS_4","EPDS_5",
                                                     "EPDS_6","EPDS_7","EPDS_8","EPDS_9","EPDS_10"))

summary(data_qualtrics_CFA_ZHONG_Model_fitW, standardized=TRUE, fit.measures=TRUE)
```
Fitting the model with MLE:
```{r results='hide'}
data_qualtrics_CFA_ZHONG_Model_fitM <- cfa(data_qualtrics_CFA_ZHONG_Model, 
                                           data=data_qualtrics_CFA60)

summary(data_qualtrics_CFA_ZHONG_Model_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### BROWERS MODEL
```{r}
data_qualtrics_CFA_BROWERS_Model <- ' depression  =~ EPDS_1 + EPDS_2 + EPDS_8
                                    anxiety =~ EPDS_3 + EPDS_4 + EPDS_5
                                    selfharm =~EPDS_10'     
```
Fitting the model with WLSMV:
```{r results='hide'}
data_qualtrics_CFA_BROWERS_Model_fitW <- cfa(data_qualtrics_CFA_BROWERS_Model, 
                                             data=data_qualtrics_CFA60,estimator="WLSMV", 
                                             ordered=c("EPDS_1", "EPDS_2","EPDS_3","EPDS_4","EPDS_5",
                                                       "EPDS_6","EPDS_7","EPDS_8","EPDS_9","EPDS_10"))

summary(data_qualtrics_CFA_BROWERS_Model_fitW, standardized=TRUE, fit.measures=TRUE)
```
Warning is before model was not identified. This was noted in paper. 
Fitting the model with MLE:
```{r results='hide'}
data_qualtrics_CFA_BROWERS_Model_fitM <- cfa(data_qualtrics_CFA_BROWERS_Model, 
                                             data=data_qualtrics_CFA60)

summary(data_qualtrics_CFA_BROWERS_Model_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### TUOHY MODEL
```{r}
data_qualtrics_CFA_TUOHY_Model <- ' anhedonia =~ EPDS_1 + EPDS_2 
                                    anxiety =~ EPDS_3 + EPDS_4 + EPDS_5
                                    depression =~ EPDS_7 + EPDS_8 + EPDS_9 + EPDS_10 ' 
```
Fitting the model with WLSMV:
```{r results='hide'}
data_qualtrics_CFA_TUOHY_Model_fitW <- cfa(data_qualtrics_CFA_TUOHY_Model,
                                           data=data_qualtrics_CFA60,estimator="WLSMV", 
                                           ordered=c("EPDS_1", "EPDS_2","EPDS_3","EPDS_4",
                                                     "EPDS_5",
                                                     "EPDS_6", "EPDS_7", "EPDS_8", "EPDS_9", 
                                                     "EPDS_10"))

summary(data_qualtrics_CFA_TUOHY_Model_fitW, standardized=TRUE, fit.measures=TRUE)
```
Fitting the model with MLE:
```{r results='hide'}
data_qualtrics_CFA_TUOHY_Model_fitM <- cfa(data_qualtrics_CFA_TUOHY_Model,
                                           data=data_qualtrics_CFA60)

summary(data_qualtrics_CFA_TUOHY_Model_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### KUBOTA MODEL
```{r}
data_qualtrics_CFA_KUBOTA_Model <- ' anhedonia =~ EPDS_1 + EPDS_2 
                                    anxiety =~ EPDS_3 + EPDS_4 + EPDS_5
                                    depression =~ EPDS_7 + EPDS_8 + EPDS_9' 
```
Fitting the model with WLSMV:
```{r results='hide'}
data_qualtrics_CFA_KUBOTA_Model_fitW <- cfa(data_qualtrics_CFA_KUBOTA_Model, 
                                            data=data_qualtrics_CFA60,estimator="WLSMV",
                                            ordered=c("EPDS_1", "EPDS_2","EPDS_3","EPDS_4","EPDS_5",
                                                      "EPDS_6", "EPDS_7", "EPDS_8", "EPDS_9"))

summary(data_qualtrics_CFA_KUBOTA_Model_fitW, standardized=TRUE, fit.measures=TRUE)
```
Fitting the model with MLE:
```{r results='hide'}
data_qualtrics_CFA_KUBOTA_Model_fitM <- cfa(data_qualtrics_CFA_KUBOTA_Model, 
                                            data=data_qualtrics_CFA60)

summary(data_qualtrics_CFA_KUBOTA_Model_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### ONE FACTOR
```{r}
data_qualtrics_CFA_ONEF_Model <- ' depression =~ EPDS_1 + EPDS_2 + EPDS_3 + EPDS_4 + EPDS_5 + EPDS_6 + 
EPDS_7 + EPDS_8 + EPDS_9 + EPDS_10 '  
```

```{r results='hide'}
data_qualtrics_CFA_ONEF_Model_fitW <- cfa(data_qualtrics_CFA_ONEF_Model, 
                                          data=data_qualtrics_CFA60,estimator="WLSMV", 
                                          ordered=c("EPDS_1", "EPDS_2","EPDS_3","EPDS_4","EPDS_5",
                                                    "EPDS_6", "EPDS_7", "EPDS_8", "EPDS_9", "EPDS_10"))

summary(data_qualtrics_CFA_ONEF_Model_fitW, standardized=TRUE, fit.measures=TRUE)
```
Fitting the model with MLE:
```{r results='hide'}
data_qualtrics_CFA_ONEF_Model_fitM <- cfa(data_qualtrics_CFA_ONEF_Model, data=data_qualtrics_CFA60)

summary(data_qualtrics_CFA_ONEF_Model_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### LAU MODEL
```{r}
data_qualtrics_CFA_LAU_Model <- ' anhedonia =~ EPDS_1 + EPDS_2 
                                    anxiety =~ EPDS_3 + EPDS_4 + EPDS_5
                                    depression =~ EPDS_6 + EPDS_7 + EPDS_8 + EPDS_9 + EPDS_10' 
```
Fitting the model with WLSMV:
```{r results='hide'}
data_qualtrics_CFA_LAU_Model_fitW <- cfa(data_qualtrics_CFA_LAU_Model, 
                                         data=data_qualtrics_CFA60,estimator="WLSMV", 
                                         ordered=c("EPDS_1", "EPDS_2","EPDS_3","EPDS_4","EPDS_5",
                                                   "EPDS_6", "EPDS_7", "EPDS_8", "EPDS_9", "EPDS_10"))

summary(data_qualtrics_CFA_LAU_Model_fitW, standardized=TRUE, fit.measures=TRUE)
```

```{r results='hide'}
data_qualtrics_CFA_LAU_Model_fitM <- cfa(data_qualtrics_CFA_LAU_Model, data=data_qualtrics_CFA60)

summary(data_qualtrics_CFA_LAU_Model_fitM, standardized=TRUE, fit.measures=TRUE)
```

## Other descriptives 

```{r}
data_qualtrics$EPDS3A = data_qualtrics$EPDS_3 + data_qualtrics$EPDS_4 + data_qualtrics$EPDS_5 
psych::describe(data_qualtrics$EPDS3A)
```

How many with EPDS 3A score of 4 or more 
```{r}
sum(data_qualtrics$EPDS3A>3, na.rm=TRUE)
```

How many with EPDS 3A score of 6 or more 
```{r}
sum(data_qualtrics$EPDS3A>5, na.rm=TRUE)
```

How many with total EPDS less than 11
```{r}
sum(data_qualtrics$EPDS_Total<11, na.rm=TRUE)
```

How many participants with EPDS 3A more than 3 and total EPDS over less than 11
```{r}
length(data_qualtrics$partticipantID[data_qualtrics$EPDS3A>3 & data_qualtrics$EPDS_Total<11])
```

How many participants with EPDS 3A more than 5 and total EPDS over less than 11
```{r}
length(data_qualtrics$partticipantID[data_qualtrics$EPDS3A>5 & data_qualtrics$EPDS_Total<11])
```

Same but with threshold 13 or more 

```{r}
length(data_qualtrics$partticipantID[data_qualtrics$EPDS3A>3 & data_qualtrics$EPDS_Total<13])
```

```{r}
length(data_qualtrics$partticipantID[data_qualtrics$EPDS3A>5 & data_qualtrics$EPDS_Total<13])
```


# dHCP PRENATAL SAMPLE 
(May also be referred to as antenatal in code) 

## Initial descriptives - dHCP Prenatal sample 
```{r}
dHCP_F1_FA <-read.csv("F1_FA.csv", header=TRUE, na.strings=c("","NA", " ", "not known"))
```

```{r}
dHCP_F1_FAClean <- janitor::remove_empty(dHCP_F1_FA, which = "rows") 
str(dHCP_F1_FAClean)
```

**Creating a dataframe with categorical variables for descriptive purposes only**
```{r}
dHCP_F1_FAClean2 <- dHCP_F1_FAClean
dHCP_F1_FAClean2$F_EPDSQ1 <- factor(dHCP_F1_FAClean2$F_EPDSQ1, levels=c(0,1,2,3),
                                labels=c("As much as..", "Not quite", "Definitely not", "Not at all"))

dHCP_F1_FAClean2$F_EPDSQ2 <- factor(dHCP_F1_FAClean2$F_EPDSQ2, levels=c(0,1,2,3),
                                labels=c("As much as..", "Rather less", "Definitely less", "Hardly"))

dHCP_F1_FAClean2$F_EPDSQ3 <- factor(dHCP_F1_FAClean2$F_EPDSQ3, levels=c(0,1,2,3),
                                labels=c("Never", "Not often", "Sometimes", "Yes, most")) 

dHCP_F1_FAClean2$F_EPDSQ4 <- factor(dHCP_F1_FAClean2$F_EPDSQ4, levels=c(0,1,2,3),
                                labels=c("No", "Hardly", "Sometimes", "Yes"))                   

dHCP_F1_FAClean2$F_EPDSQ5 <- factor(dHCP_F1_FAClean2$F_EPDSQ5, levels=c(0,1,2,3),
                                labels=c("Not at all", "Not much", "Sometimes", "Yes"))   

dHCP_F1_FAClean2$F_EPDSQ6 <- factor(dHCP_F1_FAClean2$F_EPDSQ6, levels=c(0,1,2,3),
                                labels=c("No", "No, most time..", "Sometimes", "Yes"))   

dHCP_F1_FAClean2$F_EPDSQ7 <- factor(dHCP_F1_FAClean2$F_EPDSQ7, levels=c(0,1,2,3),
                                labels=c("No", "Not very", "Sometimes", "Yes"))

dHCP_F1_FAClean2$F_EPDSQ8 <- factor(dHCP_F1_FAClean2$F_EPDSQ8, levels=c(0,1,2,3),
                                labels=c("No", "Not very", "Often", "Yes"))

dHCP_F1_FAClean2$F_EPDSQ9 <- factor(dHCP_F1_FAClean2$F_EPDSQ9, levels=c(0,1,2,3),
                                labels=c("No", "Occasionally", "Often", "Yes"))

dHCP_F1_FAClean2$F_EPDSQ10 <- factor(dHCP_F1_FAClean2$F_EPDSQ10, levels=c(0,1,2,3),
                                 labels=c("Never", "Hardly", "Sometimes", "Yes"))
```

Checking structure of dataframe.
```{r results='hide'}
str(dHCP_F1_FAClean2) 
```

Calculating % for frequency of response for each answer 
```{r}
summary(dHCP_F1_FAClean2$F_EPDSQ1)
```
Calculating percentages 
423/471 = 89.80 %  
42/471 = 8.91 %  
6/471 = 1.27 %  
0/471 = 0  %  

```{r}
summary(dHCP_F1_FAClean2$F_EPDSQ2)
```
Calculating percentages 
412/471 = 87.47 %  
48/471 = 10.19 %  
10/471 = 2.12 %  
1/471 = 0.21  %  

```{r}
summary(dHCP_F1_FAClean2$F_EPDSQ3)
```
Calculating percentages 
112/471 = 23.77 %  
231/471 = 49.04 %  
116/471 = 24.62 %  
12/471 = 2.54  %  

```{r}
summary(dHCP_F1_FAClean2$F_EPDSQ4)
```
Calculating percentages 
156/471 = 33.12 %  
151/471 = 32.05 %  
154/471 = 32.69 %  
10/471 = 2.12  %  

```{r}
summary(dHCP_F1_FAClean2$F_EPDSQ5)
```
Calculating percentages 
264/471 = 56.05 %  
132/471 = 28.02 %  
65/471 = 13.80 %  
10/471 = 2.12  %  

```{r}
summary(dHCP_F1_FAClean2$F_EPDSQ6)
```
Calculating percentages 
176/471 = 37.36 %  
211/471 = 44.79 %  
81/471 = 17.19 %  
3/471 = 0.63  %  

```{r}
summary(dHCP_F1_FAClean2$F_EPDSQ7)
```
Calculating percentages 
365/471 = 77.49 %  
64/471 = 13.58 %  
36/471 = 7.64 %  
6/471 = 1.27  %  

```{r}
summary(dHCP_F1_FAClean2$F_EPDSQ8)
```
Calculating percentages 
261/471 = 55.41 %  
173/471 = 36.73 %  
34/471 = 7.21 %  
3/471 = 0.63  %  

```{r}
summary(dHCP_F1_FAClean2$F_EPDSQ9)
```
Calculating percentages 
301/471 = 63.90 %  
151/471 = 32.05 %  
16/471 = 3.39 %   
3/471 =  0.63 %  

```{r}
summary(dHCP_F1_FAClean2$F_EPDSQ10)
```
Calculating percentages 
453/471 = 96.17 %  
15/471 = 3.18 %  
1/471 = 0.21 %  
2/471 = 0.42  %  

To double-check that these numbers are correct, also doing. All seems fine. 
```{r results="hide", warning=FALSE, comment=FALSE, message=FALSE}
((plyr::count(dHCP_F1_FAClean$F_EPDSQ1))*100)/471
((plyr::count(dHCP_F1_FAClean$F_EPDSQ2))*100)/471
((plyr::count(dHCP_F1_FAClean$F_EPDSQ3))*100)/471
((plyr::count(dHCP_F1_FAClean$F_EPDSQ4))*100)/471
((plyr::count(dHCP_F1_FAClean$F_EPDSQ5))*100)/471
((plyr::count(dHCP_F1_FAClean$F_EPDSQ6))*100)/471
((plyr::count(dHCP_F1_FAClean$F_EPDSQ7))*100)/471
((plyr::count(dHCP_F1_FAClean$F_EPDSQ8))*100)/471
((plyr::count(dHCP_F1_FAClean$F_EPDSQ9))*100)/471
((plyr::count(dHCP_F1_FAClean$F_EPDSQ10))*100)/471
```

**Going back to the main database with integers instead of categories from now on** 

## FACTOR ANALYSIS (dHCP Prenatal sample)
Creating subset of FA database without the 10th question
```{r}
dHCP_F1_FAClean9<- subset(dHCP_F1_FAClean, select=c(-F_EPDSQ10))
```

Calculating Cronbach's alpha
```{r results='hide'}
psych::alpha(dHCP_F1_FAClean9)
```

```{r}
ci.reliability(dHCP_F1_FAClean9, type="omega")
```


Need to create 2 subsets - one for EFA (40%) and one for CFA (60%)
```{r}
set.seed(999)
n=nrow(dHCP_F1_FAClean9)
dHCP_F1_FAClean9_Index = sample(1:n, size=round(0.6*n), replace=FALSE)
dHCP_F1_9_CFA60 = dHCP_F1_FAClean9 [dHCP_F1_FAClean9_Index ,]
dHCP_F1_9_EFA40 = dHCP_F1_FAClean9 [-dHCP_F1_FAClean9_Index ,]
```

```{r results='hide'}
str(dHCP_F1_9_CFA60)
str(dHCP_F1_9_EFA40)
```
CFA n=283, EFA n=188 . Total 471 

### EFA with Pearson correlation matrix (dHCP prenatal sample)

Calculating a correlation matrix and saving it 
```{r}
dHCP_F1_9_EFA40_Matrix <- cor(dHCP_F1_9_EFA40)
```

Displaying the correlation matrix using 2 decimal places
```{r}
round(dHCP_F1_9_EFA40_Matrix,2)
```

Doing Kaiser-Mayer-Olkin (KMO) measure of sampling adequacy
```{r}
KMO(dHCP_F1_9_EFA40_Matrix)
```

Doing Bartlett's test of sphrericity
```{r}
cortest.bartlett(dHCP_F1_9_EFA40_Matrix,188)
```

Calculating the determinant of the correlation matrix
```{r}
det(dHCP_F1_9_EFA40_Matrix)
```

 Get eigenvalues and scree plot
```{r}
ev_dHCP_F1_9_EFA40<- eigen(cor(dHCP_F1_9_EFA40)) 
ev_dHCP_F1_9_EFA40
```

```{r}
scree_dHCP_F1_9_EFA40 <- scree(dHCP_F1_9_EFA40)
```

Doing Parallel analysis.
First, we need to check the number of observations for EFA
```{r results='hide'}
describe(dHCP_F1_9_EFA40)
```

```{r}
parallel_dHCP_F1_9_EFA40<- fa.parallel(dHCP_F1_9_EFA40_Matrix, n.obs=188, 
                                       main="Parallel Analysis Scree Plots", fm="mrfa", 
                                       fa="fa", SMC=TRUE, quant=.95, n.iter=500)
parallel_dHCP_F1_9_EFA40
```


Doing factor analysis now 
```{r}
dHCP_F1_9_EFA40_Analysis1<-factanal (dHCP_F1_9_EFA40,2, rotation="promax", fm="mle")
print(dHCP_F1_9_EFA40_Analysis1, digits=2, cutoff=.30, sort=FALSE)
```

```{r}
dHCP_F1_9_EFA40_Analysis2<-factanal (dHCP_F1_9_EFA40,3, rotation="promax", fm="mrfa")
print(dHCP_F1_9_EFA40_Analysis2, digits=2, cutoff=.30, sort=FALSE)
```

## EFA with Polychoric correlation matrix (dHCP Prenatal sample) 

Doing the above again, with a polychoric correlation matrix this time (as per Lysdottir et al.)
```{r}
b <- psych::polychoric(dHCP_F1_9_EFA40, correct=FALSE)
dHCP_F1_9_EFA40_PolychorMatrix <- b$rho
``` 

Displaying the correlation matrix using 2 decimal places
```{r}
round(dHCP_F1_9_EFA40_PolychorMatrix,2)
```

Doing Kaiser-Mayer-Olkin (KMO) measure of sampling adequacy
```{r}
KMO(dHCP_F1_9_EFA40_PolychorMatrix)
```

Doing Bartlett's test of sphrericity
```{r}
cortest.bartlett(dHCP_F1_9_EFA40_PolychorMatrix,106)
```

Calculating the determinant of the correlation matrix
```{r}
det(dHCP_F1_9_EFA40_PolychorMatrix)
```

Get eigenvalues and scree plot
```{r}
ev_dHCP_F1_9_EFA40_PolychorMatrix<- eigen(dHCP_F1_9_EFA40_PolychorMatrix)
ev_dHCP_F1_9_EFA40_PolychorMatrix
```

```{r}
scree_dHCP_F1_9_EFA40_PolychorMatrix  <- scree(dHCP_F1_9_EFA40_PolychorMatrix)
scree_dHCP_F1_9_EFA40_PolychorMatrix 
```

```{r}
parallel_dHCP_F1_9_EFA40_PolychorMatrix<-fa.parallel(dHCP_F1_9_EFA40_PolychorMatrix,n.obs=188, 
                                                     main="Parallel Analysis Scree Plots",
                                                     fm="mrfa", 
                                                     cor="poly", quant=.95, SMC=TRUE, n.iter=500)
parallel_dHCP_F1_9_EFA40_PolychorMatrix
```

Doing the exploratory factor analysis now 
```{r}
dHCP_F1_9_EFA40_Polychor_Analysis1<-factanal (covmat=dHCP_F1_9_EFA40_PolychorMatrix,factors=2, 
                                              rotation="oblimin", fm="mle")
print(dHCP_F1_9_EFA40_Polychor_Analysis1, digits=2, cutoff=.30, sort=FALSE)
```


```{r}
dHCP_F1_9_EFA40_Polychor_Analysis2<-factanal(covmat=dHCP_F1_9_EFA40_PolychorMatrix,factors=3, 
                                             rotation="oblimin", fm="mle")
print(dHCP_F1_9_EFA40_Polychor_Analysis2, digits=2, cutoff=.30, sort=FALSE)
```

### CFA (dHCP prenatal sample)

Now doing confirmatory factor analysis 
#### From EFA - 3 FACTOR MODEL
```{r}
F1_FA_CFA_Model_3f <- ' depression  =~ F_EPDSQ7 + F_EPDSQ8   
              anhedonia =~ F_EPDSQ1
              anxiety  =~ F_EPDSQ3 + F_EPDSQ4 + F_EPDSQ5 '
```

Fitting the model with WLSMV:
```{r}
F1_FA_CFA_Model_3f_fitW <- cfa(F1_FA_CFA_Model_3f, data=dHCP_F1_9_CFA60,estimator="WLSMV", ordered=c("F_EPDSQ7","F_EPDSQ8","F_EPDSQ1","F_EPDSQ3","F_EPDSQ4","F_EPDSQ5"))
```
Warning is normal as model could not be identified. This was noted in the paper. 

```{r results='hide'}
summary(F1_FA_CFA_Model_3f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
F1_FA_CFA_Model_3f_fitM <- cfa(F1_FA_CFA_Model_3f, data=dHCP_F1_9_CFA60)
```

```{r results='hide'}
summary(F1_FA_CFA_Model_3f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### From EFA - 2 FACTOR MODEL
```{r}
F1_FA_CFA_Model_2f <- ' depression  =~ F_EPDSQ3 + F_EPDSQ4 + F_EPDSQ5 + F_EPDSQ9   
              anhedonia =~ F_EPDSQ1 + F_EPDSQ2 + F_EPDSQ7 + F_EPDSQ8'
```

Fitting the model with WLSMV:
```{r}
F1_FA_CFA_Model_2f_fitW <- cfa(F1_FA_CFA_Model_2f, data=dHCP_F1_9_CFA60,estimator="WLSMV", ordered=c("F_EPDSQ3","F_EPDSQ4","F_EPDSQ5","F_EPDSQ6","F_EPDSQ9","F_EPDSQ1", "F_EPDSQ2"))
```

```{r results='hide'}
summary(F1_FA_CFA_Model_2f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
F1_FA_CFA_Model_2f_fitM <- cfa(F1_FA_CFA_Model_2f, data=dHCP_F1_9_CFA60)
```

```{r results='hide'}
summary(F1_FA_CFA_Model_2f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### BROWERS 2 Factor Model 
```{r}
F1_FA_BROWERS_Model_2f <- ' depression  =~ F_EPDSQ1 + F_EPDSQ2 + F_EPDSQ8  
            anxiety =~ F_EPDSQ3 + F_EPDSQ4 + F_EPDSQ5'
```

Fitting the model with WLSMV:
```{r}
F1_FA_BROWERS_Model_2f_fitW <- cfa(F1_FA_BROWERS_Model_2f, data=dHCP_F1_9_CFA60,estimator="WLSMV",
                                   ordered=c("F_EPDSQ1","F_EPDSQ2","F_EPDSQ8","F_EPDSQ3", "F_EPDSQ4",
                                             "F_EPDSQ5"))
```

```{r results='hide'}
summary(F1_FA_BROWERS_Model_2f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
F1_FA_BROWERS_Model_2f_fitM <- cfa(F1_FA_BROWERS_Model_2f, data=dHCP_F1_9_CFA60)
```

```{r results='hide'}
summary(F1_FA_BROWERS_Model_2f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### KUBOTA 3 Factor Model 
```{r}
F1_FA_KUBOTA_Model_3f <- 'anhedonia =~ F_EPDSQ1 + F_EPDSQ2
            anxiety =~ F_EPDSQ3 + F_EPDSQ4 + F_EPDSQ5
            depression  =~ F_EPDSQ7 + F_EPDSQ8 + F_EPDSQ9'
```

Fitting the model with WLSMV:
```{r}
F1_FA_KUBOTA_Model_3f_fitW <- cfa(F1_FA_KUBOTA_Model_3f, data=dHCP_F1_9_CFA60,estimator="WLSMV",
                                  ordered=c("F_EPDSQ1","F_EPDSQ2","F_EPDSQ3","F_EPDSQ4", "F_EPDSQ5", 
                                            "F_EPDSQ7", "F_EPDSQ8", "F_EPDSQ9"))
```

```{r results='hide'}
summary(F1_FA_KUBOTA_Model_3f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
F1_FA_KUBOTA_Model_3f_fitM <- cfa(F1_FA_KUBOTA_Model_3f, data=dHCP_F1_9_CFA60)
```

```{r results='hide'}
summary(F1_FA_KUBOTA_Model_3f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### COX 1 Factor Model 
```{r}
F1_FA_COX_Model_1f <- 'depression =~ F_EPDSQ1 + F_EPDSQ2 + F_EPDSQ3 + F_EPDSQ4 + F_EPDSQ5 + F_EPDSQ6 + 
F_EPDSQ7 + F_EPDSQ8 + F_EPDSQ9'
```

Fitting the model with WLSMV:
```{r}
F1_FA_COX_Model_1f_fitW <- cfa(F1_FA_COX_Model_1f, data=dHCP_F1_9_CFA60,estimator="WLSMV", 
                               ordered=c("F_EPDSQ1","F_EPDSQ2","F_EPDSQ3","F_EPDSQ4", "F_EPDSQ5",
                                         "F_EPDSQ6",
                                         "F_EPDSQ7", "F_EPDSQ8", "F_EPDSQ9"))
```

```{r results='hide'}
summary(F1_FA_COX_Model_1f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
F1_FA_COX_Model_1f_fitM <- cfa(F1_FA_COX_Model_1f, data=dHCP_F1_9_CFA60)
```

```{r results='hide'}
summary(F1_FA_COX_Model_1f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### PHILLIPS Factor Model 
```{r}
F1_FA_PHILLIPS_Model_2f <- ' depression  =~ F_EPDSQ1 + F_EPDSQ2 + F_EPDSQ6 + F_EPDSQ7 + F_EPDSQ8 +
                              F_EPDSQ9    
                              anxiety =~ F_EPDSQ3 + F_EPDSQ4 + F_EPDSQ5'
```

Fitting the model with WLSMV:
```{r}
F1_FA_PHILLIPS_Model_2f_fitW <- cfa(F1_FA_PHILLIPS_Model_2f, data=dHCP_F1_9_CFA60,estimator="WLSMV",
                                    ordered=c("F_EPDSQ1","F_EPDSQ2","F_EPDSQ6","F_EPDSQ7","F_EPDSQ8",
                                              "F_EPDSQ9","F_EPDSQ3", "F_EPDSQ4", "F_EPDSQ5"))
```

```{r results='hide'}
summary(F1_FA_PHILLIPS_Model_2f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
F1_FA_PHILLIPS_Model_2f_fitM <- cfa(F1_FA_PHILLIPS_Model_2f, data=dHCP_F1_9_CFA60)
```

```{r results='hide'}
summary(F1_FA_PHILLIPS_Model_2f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### ZHONG Factor Model 
```{r}
F1_FA_ZHONG_Model_2f <- ' depression  =~ F_EPDSQ3 + F_EPDSQ4 + F_EPDSQ5 + F_EPDSQ6 + F_EPDSQ7 +
F_EPDSQ8 + F_EPDSQ9  
            anhedonia =~ F_EPDSQ1 + F_EPDSQ2'
```

Fitting the model with WLSMV:
```{r}
F1_FA_ZHONG_Model_2f_fitW <- cfa(F1_FA_ZHONG_Model_2f, data=dHCP_F1_9_CFA60,estimator="WLSMV",
                                 ordered=c("F_EPDSQ1","F_EPDSQ2","F_EPDSQ6","F_EPDSQ7","F_EPDSQ8",
                                           "F_EPDSQ9", 
                                           "F_EPDSQ3", "F_EPDSQ4", "F_EPDSQ5"))
```

```{r results='hide'}
summary(F1_FA_ZHONG_Model_2f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
F1_FA_ZHONG_Model_2f_fitM <- cfa(F1_FA_ZHONG_Model_2f, data=dHCP_F1_9_CFA60)
```

```{r results='hide'}
summary(F1_FA_ZHONG_Model_2f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### TUOHY Factor Model 
```{r}
F1_FA_TUOHY_Model_2f <- ' depression  =~ F_EPDSQ7 + F_EPDSQ8 + F_EPDSQ9  
            anhedonia =~ F_EPDSQ1 + F_EPDSQ2
            anxiety=~ F_EPDSQ3 + F_EPDSQ4 + F_EPDSQ5'
```

Fitting the model with WLSMV:
```{r}
F1_FA_TUOHY_Model_2f_fitW <- cfa(F1_FA_TUOHY_Model_2f, data=dHCP_F1_9_CFA60,estimator="WLSMV",
                                 ordered=c("F_EPDSQ1","F_EPDSQ2","F_EPDSQ6","F_EPDSQ7","F_EPDSQ8",
                                           "F_EPDSQ9", 
                                           "F_EPDSQ3", "F_EPDSQ4", "F_EPDSQ5"))
```

```{r results='hide'}
summary(F1_FA_TUOHY_Model_2f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
F1_FA_TUOHY_Model_2f_fitM <- cfa(F1_FA_TUOHY_Model_2f, data=dHCP_F1_9_CFA60)
```

```{r results='hide'}
summary(F1_FA_TUOHY_Model_2f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### LAU Factor Model 

```{r}
F1_FA_LAU_Model_2f <- ' depression  =~ F_EPDSQ6 + F_EPDSQ7 + F_EPDSQ8 + F_EPDSQ9  
            anhedonia=~ F_EPDSQ1 + F_EPDSQ2
            anxiety=~ F_EPDSQ3 + F_EPDSQ4 + F_EPDSQ5'
```

Fitting the model with WLSMV:

```{r}
F1_FA_LAU_Model_2f_fitW <- cfa(F1_FA_LAU_Model_2f, data=dHCP_F1_9_CFA60,estimator="WLSMV",
                               ordered=c("F_EPDSQ1", "F_EPDSQ2", "F_EPDSQ3", "F_EPDSQ4", "F_EPDSQ5",
                                         "F_EPDSQ6","F_EPDSQ7", "F_EPDSQ8", "F_EPDSQ9"))
```


```{r results='hide'}
summary(F1_FA_LAU_Model_2f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
F1_FA_LAU_Model_2f_fitM <- cfa(F1_FA_LAU_Model_2f, data=dHCP_F1_9_CFA60)
```

```{r results='hide'}
summary(F1_FA_LAU_Model_2f_fitM, standardized=TRUE, fit.measures=TRUE)
```

# dHCP POSTNATAL sample 

## Initial descriptives and setup (dHCP postnatal sample)

Loading dataframe 
```{r}
dHCP_N1_FA <-read.csv("N1_FA.csv", header=TRUE, na.strings=c("","NA", " ", "not known"))
```

Removing empty rows 
```{r}
dHCP_N1_FAClean <- janitor::remove_empty(dHCP_N1_FA, which = "rows") 
```

```{r results='hide'}
str(dHCP_N1_FAClean)
```

**Creating a dataframe with categorical variables for descriptive purposes only**
```{r}
dHCP_N1_FAClean2 <- dHCP_N1_FAClean
dHCP_N1_FAClean2$N_EPDSQ1 <- factor(dHCP_N1_FAClean2$N_EPDSQ1, levels=c(0,1,2,3),
                                labels=c("As much as..", "Not quite", "Definitely not", "Not at all"))

dHCP_N1_FAClean2$N_EPDSQ2 <- factor(dHCP_N1_FAClean2$N_EPDSQ2, levels=c(0,1,2,3),
                                labels=c("As much as..", "Rather less", "Definitely less", "Hardly"))

dHCP_N1_FAClean2$N_EPDSQ3 <- factor(dHCP_N1_FAClean2$N_EPDSQ3, levels=c(0,1,2,3),
                                labels=c("Never", "Not often", "Sometimes", "Yes, most")) 

dHCP_N1_FAClean2$N_EPDSQ4 <- factor(dHCP_N1_FAClean2$N_EPDSQ4, levels=c(0,1,2,3),
                                labels=c("No", "Hardly", "Sometimes", "Yes"))                   

dHCP_N1_FAClean2$N_EPDSQ5 <- factor(dHCP_N1_FAClean2$N_EPDSQ5, levels=c(0,1,2,3),
                                labels=c("Not at all", "Not much", "Sometimes", "Yes"))   

dHCP_N1_FAClean2$N_EPDSQ6 <- factor(dHCP_N1_FAClean2$N_EPDSQ6, levels=c(0,1,2,3),
                                labels=c("No", "No, most time..", "Sometimes", "Yes"))   

dHCP_N1_FAClean2$N_EPDSQ7 <- factor(dHCP_N1_FAClean2$N_EPDSQ7, levels=c(0,1,2,3),
                                labels=c("No", "Not very", "Sometimes", "Yes"))

dHCP_N1_FAClean2$N_EPDSQ8 <- factor(dHCP_N1_FAClean2$N_EPDSQ8, levels=c(0,1,2,3),
                                labels=c("No", "Not very", "Often", "Yes"))

dHCP_N1_FAClean2$N_EPDSQ9 <- factor(dHCP_N1_FAClean2$N_EPDSQ9, levels=c(0,1,2,3),
                                labels=c("No", "Occasionally", "Often", "Yes"))

dHCP_N1_FAClean2$N_EPDSQ10 <- factor(dHCP_N1_FAClean2$N_EPDSQ10, levels=c(0,1,2,3),
                                 labels=c("Never", "Hardly", "Sometimes", "Yes"))
```

Checking structure of dataframe.
```{r resuls='hide'}
str(dHCP_N1_FAClean2) 
```

Calculating % for frequency of response for each answer 
```{r}
summary(dHCP_N1_FAClean2$N_EPDSQ1)
```
Calculating percentages 
517/637 = 81.16 %  
98/637 = 15.38 %  
17/637 = 2.66 %  
5/637 = 0.78 %  

```{r}
summary(dHCP_N1_FAClean2$N_EPDSQ2)
```
Calculating percentages 
537/637 = 84.30 %  
82/637 = 12.87 %  
12/637= 1.88 %  
6/637 = 0.94 %  

```{r}
summary(dHCP_N1_FAClean2$N_EPDSQ3)
```
Calculating percentages 
168/637 = 26.37 %  
276/637= 43.32 %  
178/637 = 27.94 %  
15/637 = 2.35 %  

```{r}
summary(dHCP_N1_FAClean2$N_EPDSQ4)
```
Calculating percentages 
225/637 = 35.32 %   
207/637 = 32.49 %  
182/637 = 28.57 %  
23/637 = 3.61 %  

```{r}
summary(dHCP_N1_FAClean2$N_EPDSQ5)
```
Calculating percentages 
343/637 = 53.84 %  
188/637 = 29.51 %  
97/637 = 15.22 %  
9/637 = 1.41 %  

```{r}
summary(dHCP_N1_FAClean2$N_EPDSQ6)
```
Calculating percentages 
187/637 = 29.35 %  
315/637 = 49.45 %  
126/637 = 19.78 %  
9/637 = 1.41%  

```{r}
summary(dHCP_N1_FAClean2$N_EPDSQ7)
```
Calculating percentages 
467/637 = 73.31 %  
107/637 = 16.79 %  
53/637= 8.32 %  
10/637 = 1.56 %  

```{r}
summary(dHCP_N1_FAClean2$N_EPDSQ8)
```
Calculating percentages 
341/637 = 53.53 %  
245/637 = 38.46 %  
48/637 = 7.53 %  
3/637 = 0.47 %  

```{r}
summary(dHCP_N1_FAClean2$N_EPDSQ9)
```
Calculating percentages 
351/637 = 55.10 %  
251/637 = 39.40 %  
29/637 = 4.55 %  
6/637 = 0.94 %  

```{r}
summary(dHCP_N1_FAClean2$N_EPDSQ10)
```
Calculating percentages 
617/637 = 96.86 %  
12/637 = 1.88 %  
8/637 = 1.25 %  
0/637 = 0 %  

To double-check that these numbers are correct, also doing. All seems fine. 
```{r results="hide", warning=FALSE, comment=FALSE, message=FALSE}
((plyr::count(dHCP_N1_FAClean2$N_EPDSQ1))*100)/637
((plyr::count(dHCP_N1_FAClean2$N_EPDSQ2))*100)/637
((plyr::count(dHCP_N1_FAClean2$N_EPDSQ3))*100)/637
((plyr::count(dHCP_N1_FAClean2$N_EPDSQ4))*100)/637
((plyr::count(dHCP_N1_FAClean2$N_EPDSQ5))*100)/637
((plyr::count(dHCP_N1_FAClean2$N_EPDSQ6))*100)/637
((plyr::count(dHCP_N1_FAClean2$N_EPDSQ7))*100)/637
((plyr::count(dHCP_N1_FAClean2$N_EPDSQ8))*100)/637
((plyr::count(dHCP_N1_FAClean2$N_EPDSQ9))*100)/637
((plyr::count(dHCP_N1_FAClean2$N_EPDSQ10))*100)/637
```

**Going back to the main database with integers instead of categories from now on** 

## FACTOR ANALYSIS (dHCP Postnatal sample)
Creating subset of FA database without the 10th question
```{r}
dHCP_N1_FAClean9<- subset(dHCP_N1_FAClean, select=c(-N_EPDSQ10))
```

Calculating Cronbach's alpha
```{r results="hide"}
psych::alpha(dHCP_N1_FAClean9)
```

Calculating McDonald's omega 
```{r}
ci.reliability(dHCP_N1_FAClean9, type="omega")
```



Need to create 2 subsets - one for EFA (40%) and one for CFA (60%)
```{r}
set.seed(6740)
n=nrow(dHCP_N1_FAClean9)
dHCP_N1_FAClean9_Index = sample(1:n, size=round(0.6*n), replace=FALSE)
dHCP_N1_9_CFA60 = dHCP_N1_FAClean9 [dHCP_N1_FAClean9_Index ,]
dHCP_N1_9_EFA40 = dHCP_N1_FAClean9 [-dHCP_N1_FAClean9_Index ,]
```

```{r results='hide'}
str(dHCP_N1_9_CFA60)
str(dHCP_N1_9_EFA40)
```
CFA n=382, EFA n=255 . Total 637. 

### EFA with Pearson correlation matrix (dHCP Postnatal sample)

Calculating a correlation matrix and saving it 
```{r}
dHCP_N1_9_EFA40_Matrix <- cor(dHCP_N1_9_EFA40)
```

Displaying the correlation matrix using 2 decimal places. 
Checking if there are any above 9, to avoid multicollinearity (there are not) or any that don't correlate at all with other (there are not). 
```{r}
round(dHCP_N1_9_EFA40_Matrix,2)
```

Doing Kaiser-Mayer-Olkin (KMO) measure of sampling adequacy.KMO measures of sampling adequacy were >.8, well above the acceptable limit of .5.  
```{r}
KMO(dHCP_N1_9_EFA40_Matrix)
```

Doing Bartlett's test of sphrericity.Bartlett’s test of sphericity p<.05 indicated that the correlations between items were sufficiently large for factor analysis
```{r}
cortest.bartlett(dHCP_N1_9_EFA40_Matrix,188)
```

Calculating the determinant of the correlation matrix. The determinant of the correlation matrix was .., greater than the necessary value of .00001.
 
```{r}
det(dHCP_N1_9_EFA40_Matrix)
```

 Get eigenvalues and scree plot
```{r}
ev_dHCP_N1_9_EFA40<- eigen(cor(dHCP_N1_9_EFA40)) 
ev_dHCP_N1_9_EFA40
```

```{r}
scree_dHCP_N1_9_EFA40 <- scree(dHCP_N1_9_EFA40)
```

Doing Parallel analysis.
First, we need to check the number of observations for EFA.
```{r results='hide'}
describe(dHCP_N1_9_EFA40)
```

```{r}
parallel_dHCP_N1_9_EFA40<- fa.parallel(dHCP_N1_9_EFA40_Matrix, n.obs=255, 
                                       main="Parallel Analysis Scree Plots", fm="mrfa", fa="fa", 
                                       SMC=TRUE, quant=.95, n.iter=500)
parallel_dHCP_N1_9_EFA40
```

Now doing the EFA
```{r}
dHCP_N1_9_EFA40_Analysis1<-factanal (dHCP_N1_9_EFA40,2, rotation="promax", fm="mle")
print(dHCP_N1_9_EFA40_Analysis1, digits=2, cutoff=.30, sort=FALSE)
```

```{r}
dHCP_N1_9_EFA40_Analysis2<-factanal (dHCP_N1_9_EFA40,3, rotation="promax", fm="mrfa")
print(dHCP_N1_9_EFA40_Analysis2, digits=2, cutoff=.30, sort=FALSE)
```

### EFA with Polychoric correlation matrix (dHCP Postnatal sample)

Trying to do the above again, with a polychoric correlation matrix this time (as per Lysdottir et al.). 
```{r}
c <- psych::polychoric(dHCP_N1_9_EFA40, correct=FALSE) 
dHCP_N1_9_EFA40_PolychorMatrix <- c$rho
``` 


Displaying the correlation matrix using 2 decimal places
```{r}
round(dHCP_N1_9_EFA40_PolychorMatrix,2)
```

Doing Kaiser-Mayer-Olkin (KMO) measure of sampling adequacy.KMO measures of sampling adequacy were well above the acceptable limit of .5.  
```{r}
KMO(dHCP_N1_9_EFA40_PolychorMatrix)
```

Doing Bartlett's test of sphrericity
```{r}
cortest.bartlett(dHCP_N1_9_EFA40_PolychorMatrix,106)
```

Calculating the determinant of the correlation matrix
```{r}
det(dHCP_N1_9_EFA40_PolychorMatrix)
```

 Get eigenvalues and scree plot.Checking the tail end of eigenvalues to make sure all are non-negative 
 All are >0 , which means that we have obtained a proper correlation matrix. 
Check eigenvalues >1
```{r}
ev_dHCP_N1_9_EFA40_PolychorMatrix<- eigen(dHCP_N1_9_EFA40_PolychorMatrix)
ev_dHCP_N1_9_EFA40_PolychorMatrix
```

```{r}
scree_dHCP_N1_9_EFA40_PolychorMatrix  <- scree(dHCP_N1_9_EFA40_PolychorMatrix)
scree_dHCP_N1_9_EFA40_PolychorMatrix 
```

```{r}
parallel_dHCP_N1_9_EFA40_PolychorMatrix<-fa.parallel(dHCP_N1_9_EFA40_PolychorMatrix, n.obs=255, 
                                                     main="Parallel Analysis Scree Plots", fa="fa",
                                                     fm="mrfa",cor="poly", quant=.95, SMC=TRUE, 
                                                     n.iter=500)
parallel_dHCP_N1_9_EFA40_PolychorMatrix
```

Doing the exploratory factor analysis now 
```{r}
dHCP_N1_9_EFA40_Polychor_Analysis1<-factanal (covmat=dHCP_N1_9_EFA40_PolychorMatrix,factors=2, 
                                              rotation="oblimin", fm="mle")
print(dHCP_N1_9_EFA40_Polychor_Analysis1, digits=2, cutoff=.30, sort=FALSE)
```

```{r}
dHCP_N1_9_EFA40_Polychor_Analysis2<-factanal(covmat=dHCP_N1_9_EFA40_PolychorMatrix,factors=3,
                                             rotation="oblimin", fm="mle")
print(dHCP_N1_9_EFA40_Polychor_Analysis2, digits=2, cutoff=.30, sort=FALSE)
```

### CFA (dHCP Postnatal sample)

Doing confirmatory factor analysis. Hiding results as they would take up too much space. 
#### From EFA - 3 FACTOR MODEL
```{r}
N1_FA_CFA_Model_3f <- ' depression  =~ N_EPDSQ8 + N_EPDSQ9   
              anhedonia =~ N_EPDSQ1 + N_EPDSQ2 
              anxiety  =~ N_EPDSQ3 + N_EPDSQ4 + N_EPDSQ5 '
```

Fitting the model with WLSMV:
```{r}
N1_FA_CFA_Model_3f_fitW <- cfa(N1_FA_CFA_Model_3f, data=dHCP_N1_9_CFA60,estimator="WLSMV", 
                               ordered=TRUE)
```

```{r results='hide'}
summary(N1_FA_CFA_Model_3f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
N1_FA_CFA_Model_3f_fitM <- cfa(N1_FA_CFA_Model_3f, data=dHCP_N1_9_CFA60)
```

```{r results='hide'}
summary(N1_FA_CFA_Model_3f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### EFA 2 factor model

From EFA - 2 FACTOR MODEL
```{r}
N1_FA_CFA_Model_2f <- ' depression  =~  N_EPDSQ1 + N_EPDSQ2 + N_EPDSQ7 + N_EPDSQ8 + N_EPDSQ9   
              anxiety  =~ N_EPDSQ3 + N_EPDSQ4 + N_EPDSQ5 '
```

Fitting the model with WLSMV:
```{r}
N1_FA_CFA_Model_2f_fitW <- cfa(N1_FA_CFA_Model_2f, data=dHCP_N1_9_CFA60,estimator="WLSMV", 
                               ordered=TRUE)
```

```{r results='hide'}
summary(N1_FA_CFA_Model_2f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
N1_FA_CFA_Model_2f_fitM <- cfa(N1_FA_CFA_Model_2f, data=dHCP_N1_9_CFA60)
```

```{r results='hide'}
summary(N1_FA_CFA_Model_2f_fitM, standardized=TRUE, fit.measures=TRUE)
```


#### BROWERS 2 Factor Model 
```{r}
N1_FA_BROWERS_Model_2f <- ' depression  =~ N_EPDSQ1 + N_EPDSQ2 + N_EPDSQ8  
            anxiety =~ N_EPDSQ3 + N_EPDSQ4 + N_EPDSQ5'
```

Fitting the model with WLSMV:
```{r}
N1_FA_BROWERS_Model_2f_fitW <- cfa(N1_FA_BROWERS_Model_2f, data=dHCP_N1_9_CFA60,estimator="WLSMV",
                                   ordered=c("N_EPDSQ1","N_EPDSQ2","N_EPDSQ8","N_EPDSQ3",
                                             "N_EPDSQ4", "N_EPDSQ5"))
```

```{r results='hide'}
summary(N1_FA_BROWERS_Model_2f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
N1_FA_BROWERS_Model_2f_fitM <- cfa(N1_FA_BROWERS_Model_2f, data=dHCP_N1_9_CFA60)
```

```{r results='hide'}
summary(N1_FA_BROWERS_Model_2f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### KUBOTA 3 Factor Model 
```{r}
N1_FA_KUBOTA_Model_3f <- 'anhedonia =~ N_EPDSQ1 + N_EPDSQ2
            anxiety =~ N_EPDSQ3 + N_EPDSQ4 + N_EPDSQ5
            depression  =~ N_EPDSQ7 + N_EPDSQ8 + N_EPDSQ9'
```

Fitting the model with WLSMV:
```{r}
N1_FA_KUBOTA_Model_3f_fitW <- cfa(N1_FA_KUBOTA_Model_3f, data=dHCP_N1_9_CFA60,estimator="WLSMV",
                                  ordered=c("N_EPDSQ1","N_EPDSQ2","N_EPDSQ3","N_EPDSQ4", 
                                            "N_EPDSQ5", "N_EPDSQ7", 
                                            "N_EPDSQ8", "N_EPDSQ9"))
```

```{r results='hide'}
summary(N1_FA_KUBOTA_Model_3f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
N1_FA_KUBOTA_Model_3f_fitM <- cfa(N1_FA_KUBOTA_Model_3f, data=dHCP_N1_9_CFA60)
```

```{r results='hide'}
summary(N1_FA_KUBOTA_Model_3f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### COX 1 Factor Model 
```{r}
N1_FA_COX_Model_1f <- 'depression =~ N_EPDSQ1 + N_EPDSQ2 + N_EPDSQ3 + N_EPDSQ4 + N_EPDSQ5 +
N_EPDSQ6 + N_EPDSQ7 + N_EPDSQ8 + N_EPDSQ9'
```

Fitting the model with WLSMV:
```{r}
N1_FA_COX_Model_1f_fitW <- cfa(N1_FA_COX_Model_1f, data=dHCP_N1_9_CFA60,estimator="WLSMV", 
                               ordered=c("N_EPDSQ1","N_EPDSQ2","N_EPDSQ3","N_EPDSQ4", "N_EPDSQ5",
                                         "N_EPDSQ6", "N_EPDSQ7", 
                                         "N_EPDSQ8", "N_EPDSQ9"))
```

```{r results='hide'}
summary(N1_FA_COX_Model_1f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
N1_FA_COX_Model_1f_fitM <- cfa(N1_FA_COX_Model_1f, data=dHCP_N1_9_CFA60)
```

```{r results='hide'}
summary(N1_FA_COX_Model_1f_fitM, standardized=TRUE, fit.measures=TRUE)
```


#### PHILLIPS 2 Factor Model 
```{r}
N1_FA_PHILLIPS_Model_3f <- 'anxiety =~ N_EPDSQ3 + N_EPDSQ4 + N_EPDSQ5
            depression  =~ N_EPDSQ1 + N_EPDSQ2 + N_EPDSQ6 + N_EPDSQ7 + N_EPDSQ8 + N_EPDSQ9'
```

Fitting the model with WLSMV:
```{r}
N1_FA_PHILLIPS_Model_3f_fitW <- cfa(N1_FA_PHILLIPS_Model_3f, data=dHCP_N1_9_CFA60,estimator="WLSMV",
                                    ordered=c("N_EPDSQ1","N_EPDSQ2","N_EPDSQ3","N_EPDSQ4",
                                              "N_EPDSQ5", 
                                              "N_EPDSQ7", "N_EPDSQ8", "N_EPDSQ9"))
```

```{r results='hide'}
summary(N1_FA_PHILLIPS_Model_3f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
N1_FA_PHILLIPS_Model_3f_fitM <- cfa(N1_FA_PHILLIPS_Model_3f, data=dHCP_N1_9_CFA60)
```

```{r results='hide'}
summary(N1_FA_PHILLIPS_Model_3f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### ZHONG 2 Factor Model 
```{r}
N1_FA_ZHONG_Model_3f <- 'anhedonia =~ N_EPDSQ1 + N_EPDSQ2 
            depression =~ N_EPDSQ3 + N_EPDSQ4 + N_EPDSQ5 + N_EPDSQ6 + N_EPDSQ7 + N_EPDSQ8 + N_EPDSQ9'
```

Fitting the model with WLSMV:
```{r}
N1_FA_ZHONG_Model_3f_fitW <- cfa(N1_FA_ZHONG_Model_3f, data=dHCP_N1_9_CFA60,estimator="WLSMV",
                                 ordered=c("N_EPDSQ1","N_EPDSQ2","N_EPDSQ3","N_EPDSQ4", "N_EPDSQ5", 
                                           "N_EPDSQ7", "N_EPDSQ8", "N_EPDSQ9"))
```

```{r results='hide'}
summary(N1_FA_ZHONG_Model_3f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
N1_FA_ZHONG_Model_3f_fitM <- cfa(N1_FA_ZHONG_Model_3f, data=dHCP_N1_9_CFA60)
```

```{r results='hide'}
summary(N1_FA_ZHONG_Model_3f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### LAU 3 Factor Model 
```{r}
N1_FA_LAU_Model_3f <- 'anhedonia =~ N_EPDSQ1 + N_EPDSQ2 
            depression =~ N_EPDSQ6 + N_EPDSQ7 + N_EPDSQ8 + N_EPDSQ9
            anxiety =~ N_EPDSQ3 + N_EPDSQ4 + N_EPDSQ5'
```

Fitting the model with WLSMV:
```{r}
N1_FA_LAU_Model_3f_fitW <- cfa(N1_FA_LAU_Model_3f, data=dHCP_N1_9_CFA60,estimator="WLSMV",
                               ordered=c("N_EPDSQ1","N_EPDSQ2","N_EPDSQ3","N_EPDSQ4", "N_EPDSQ5", 
                                         "N_EPDSQ7", "N_EPDSQ8", "N_EPDSQ9"))
```

```{r results='hide'}
summary(N1_FA_LAU_Model_3f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
N1_FA_LAU_Model_3f_fitM <- cfa(N1_FA_LAU_Model_3f, data=dHCP_N1_9_CFA60)
```

```{r results='hide'}
summary(N1_FA_LAU_Model_3f_fitM, standardized=TRUE, fit.measures=TRUE)
```

#### TUOHY 3 Factor Model 
```{r}
N1_FA_TUOHY_Model_3f <- 'anhedonia =~ N_EPDSQ1 + N_EPDSQ2 
            depression =~ N_EPDSQ7 + N_EPDSQ8 + N_EPDSQ9
            anxiety =~ N_EPDSQ3 + N_EPDSQ4 + N_EPDSQ5'
```

Fitting the model with WLSMV:
```{r}
N1_FA_TUOHY_Model_3f_fitW <- cfa(N1_FA_TUOHY_Model_3f, data=dHCP_N1_9_CFA60,estimator="WLSMV",
                                 ordered=c("N_EPDSQ1","N_EPDSQ2","N_EPDSQ3","N_EPDSQ4", "N_EPDSQ5", 
                                           "N_EPDSQ7", "N_EPDSQ8", "N_EPDSQ9"))
```

```{r results='hide'}
summary(N1_FA_TUOHY_Model_3f_fitW , standardized=TRUE, fit.measures=TRUE)
```

Fitting the model with MLE:
```{r}
N1_FA_TUOHY_Model_3f_fitM <- cfa(N1_FA_TUOHY_Model_3f, data=dHCP_N1_9_CFA60)
```

```{r results='hide'}
summary(N1_FA_TUOHY_Model_3f_fitM, standardized=TRUE, fit.measures=TRUE)
```

# OVERALL SAMPLE - EXPLORATORY FACTOR ANALYSIS 

## Initial descriptives and setup (overall sample)
```{r}
OverallEFA <-read.csv("OverallEFA.csv", header=TRUE, na.strings=c("","NA", " ", "not known"))
OverallEFAClean <- janitor::remove_empty(OverallEFA, which = "cols") 
```

```{r results="hide", warning=FALSE, comment=FALSE, message=FALSE}
((plyr::count(OverallEFAClean$O_EPDS1))*100)/1190
((plyr::count(OverallEFAClean$O_EPDS2))*100)/1190
((plyr::count(OverallEFAClean$O_EPDS3))*100)/1190
((plyr::count(OverallEFAClean$O_EPDS4))*100)/1190
((plyr::count(OverallEFAClean$O_EPDS5))*100)/1190
((plyr::count(OverallEFAClean$O_EPDS6))*100)/1190
((plyr::count(OverallEFAClean$O_EPDS7))*100)/1190
((plyr::count(OverallEFAClean$O_EPDS8))*100)/1190
((plyr::count(OverallEFAClean$O_EPDS9))*100)/1190
((plyr::count(OverallEFAClean$O_EPDS10))*100)/1190
```

Calculating Cronbach's alpha
```{r results="hide"}
psych::alpha(OverallEFAClean)
```

Calculating McDonald's alpha 
```{r}
ci.reliability(OverallEFAClean, type="omega")
```


## FACTOR ANALYSIS (EFA with Polychoric correlation matrix)
```{r}
d <- psych::polychoric(OverallEFAClean, correct=FALSE) 
OverallEFAClean_PolychorMatrix <- d$rho
``` 

Displaying the correlation matrix using 2 decimal places
```{r}
round(OverallEFAClean_PolychorMatrix,2)
```

Doing Kaiser-Mayer-Olkin (KMO) measure of sampling adequacy
```{r}
KMO(OverallEFAClean_PolychorMatrix)
```

Doing Bartlett's test of sphrericity
```{r}
cortest.bartlett(OverallEFAClean_PolychorMatrix,1190)
```

Calculating the determinant of the correlation matrix
```{r}
det(OverallEFAClean_PolychorMatrix)
```

 Get eigenvalues and scree plot
```{r}
ev_OverallEFAClean_PolychorMatrix<- eigen(OverallEFAClean_PolychorMatrix)
ev_OverallEFAClean_PolychorMatrix
```

```{r}
scree_OverallEFAClean_PolychorMatrix  <- scree(OverallEFAClean_PolychorMatrix)
scree_OverallEFAClean_PolychorMatrix
```

```{r}
parallel_OverallEFAClean_PolychorMatrix<-fa.parallel(OverallEFAClean_PolychorMatrix, n.obs=1190,
                                                     main="Parallel Analysis Scree Plots", fa="fa", 
                                                     fm="mrfa",cor="poly", quant=.95, SMC=TRUE, 
                                                     n.iter=50)
parallel_OverallEFAClean_PolychorMatrix
```

Doing the exploratory factor analysis now 
```{r}
OverallEFAClean_Polychor_Analysis1<-factanal (covmat=OverallEFAClean_PolychorMatrix,factors=2, 
                                              rotation="oblimin", fm="mle")
print(OverallEFAClean_Polychor_Analysis1, digits=2, cutoff=.30, sort=FALSE)
```


```{r}
OverallEFAClean_Polychor_Analysis2<-factanal (covmat=OverallEFAClean_PolychorMatrix,factors=3,
                                              rotation="oblimin", fm="mle")
print(OverallEFAClean_Polychor_Analysis2, digits=2, cutoff=.30, sort=FALSE)
```

# EPDS 3A ANALYSIS 

## EPDS 3A for prenatal timepoint 

Loading both dataframes (for prenatal and postnatal)
```{r}
F1_dHCP <-read.csv("F1_DF_Clean.csv", header=TRUE, na.strings=c("","NA", " ", "not known"))
N1_dHCP <-read.csv("N1_DF_Clean.csv", header=TRUE, na.strings=c("","NA", " ", "not known"))
```

Descriptives
```{r}
F1_dHCP$F_EPDS3A = F1_dHCP$F_EPDSQ3 + F1_dHCP$F_EPDSQ4 + F1_dHCP$F_EPDSQ5 
psych::describe(F1_dHCP$F_EPDS3A)
```

Descriptives for each group 
```{r}
by(F1_dHCP$F_EPDS3A, F1_dHCP$ANY_ANX, stat.desc, basic = FALSE, norm =TRUE)
```

How many participants in each group
```{r}
F1_dHCP$NoAnx = F1_dHCP$ANY_ANX =="No"
F1_dHCP$YesAnx = F1_dHCP$ANY_ANX =="Yes"
summary(F1_dHCP$NoAnx)
summary(F1_dHCP$YesAnx)
```

Checking the distribution of scores (to see if they are normally distributed)
```{r}
EPDS3A_NoAnx = F1_dHCP$F_EPDS3A[F1_dHCP$ANY_ANX=="No"]
EPDS3A_YesAnx = F1_dHCP$F_EPDS3A[F1_dHCP$ANY_ANX=="Yes"]
plotNormalHistogram(EPDS3A_NoAnx)
plotNormalHistogram(EPDS3A_YesAnx)
```

How many above threshold

```{r}
sum(F1_dHCP$F_EPDS3A>3, na.rm=TRUE)
```

```{r}
sum(F1_dHCP$F_EPDS3A>5, na.rm=TRUE)
```

## EPDS 3A for postnatal timepoint 

Descriptives
```{r}
N1_dHCP$NoAnx = N1_dHCP$ANY_ANX =="No"
N1_dHCP$YesAnx = N1_dHCP$ANY_ANX =="Yes"
summary(N1_dHCP$NoAnx)
summary(N1_dHCP$YesAnx)
```

```{r}
by(N1_dHCP$N_EPDS3A, N1_dHCP$ANY_ANX, stat.desc, basic = FALSE, norm =TRUE)
```

### EPDS and history 

Loading dataframe specific to plot
```{r}
ForPlotF1 <-read.csv("ForPlotF1.csv", header=TRUE, na.strings=c("","NA", " ", "not known"))
ForPlotF1$participantID <- as.character(ForPlotF1$participantID)
```

Descriptives
```{r}
by(ForPlotF1$F_EPDS3A, ForPlotF1$History, stat.desc, basic = FALSE, norm =TRUE)
```

```{r}
ForPlotN1 <-read.csv("ForPlotN1.csv", header=TRUE, na.strings=c("","NA", " ", "not known"))
ForPlotN1$participantID <- as.character(ForPlotN1$participantID)
```

```{r}
by(ForPlotN1$N_EPDS3A, ForPlotN1$History, stat.desc, basic = FALSE, norm =TRUE)
```

# Qualtrics Plots (Additional questionnaires)
PSS here stands for Prenatal Stress Study 

Load dataframe 
```{r}
PSS <-read.csv("PSS.csv", header=TRUE, na.strings=c("","NA", " ", "not known"))
```


```{r fig.show='hide' , warning=FALSE}
p6 <- ggplot(PSS, aes(x=F_EPDS3A, y=F_STAI_S_SUM)) + geom_point(aes(colour=F_EPDS3A)) +
  labs(x="EPDS-3A", y="State Anxiety")+ ylim(10,80)
p6a <- p6 + scale_colour_hp(option="LunaLovegood")+ geom_smooth(method=lm, colour="#773745") +
  theme_light() +theme(legend.position = "none",text=element_text(size=15)) 
p6a
```

```{r fig.show='hide' , warning=FALSE}
p7 <- ggplot(PSS, aes(x=F_EPDS3A, y=F_STAI_T_SUM)) + geom_point(aes(colour=F_EPDS3A)) +
  labs(x="EPDS-3A", y="Trait Anxiety")+ ylim(10,80)
p7a <- p7 + scale_colour_hp(option="LunaLovegood")+ geom_smooth(method=lm, colour="#773745") +
  theme_light() +theme(legend.position = "none",text=element_text(size=15)) 
p7a
```

```{r fig.show='hide' , warning=FALSE}
p8<- ggplot(PSS, aes(x=F_EPDS3A, y=F_NUPDQ_TOTAL)) + geom_point(aes(colour=F_EPDS3A)) + 
  labs(x="EPDS-3A", y="NUPDQ")
p8a <- p8 + scale_colour_hp(option="LunaLovegood")+ geom_smooth(method=lm, colour="#773745") + 
  theme_light() +theme(legend.position = "none",text=element_text(size=15)) 
p8a
```

```{r fig.show='hide' , warning=FALSE}
p9<- ggplot(PSS, aes(x=F_EPDS3A, y=F_PSS_TOTAL)) + geom_point(aes(colour=F_EPDS3A)) + 
  labs(x="EPDS-3A", y="PSS")+ ylim(0,40)
p9a <- p9 + scale_colour_hp(option="LunaLovegood") + 
  theme_light() +theme(legend.position = "none",text=element_text(size=15)) 
p9a
```

```{r  warning=FALSE}
grid9a<- plot_grid(p6a, p7a, p8a, p9a)
grid9a
```

```{r}
psych::describe(PSS$F_EPDSTotal)
```


# MAIN DESCRIPTIVES dHCP 

These were done at the beginning of the analysis, but placed here in the script 

```{r}
dHCP <-read.csv("dHCP_FINAL_use.csv", header=TRUE, na.strings=c("","NA", " ", "not known"))
```

## Descriptives main database 
```{r results='hide'}
str(dHCP,list.len = ncol(dHCP))
```

Checking variables that I need for descriptives
```{r}
summary(dHCP$Highest_Perinatal_EPDS)
```

```{r}
summary(dHCP$Higest_F_EPDS) 
```

```{r}
summary(dHCP$Highest_N_EPDS)
```

```{r}
summary(dHCP$mother_ethnicity.enrolment_1)
```
 
```{r}
summary(dHCP$mother_age.enrolment_1)
```

```{r}
summary(dHCP$mother_education.enrolment_1)
```

Not leaving maternal occupation in here, as info can be identifiable. 

```{r}
summary(dHCP$mother_smokingyn.enrolment_1)
```

```{r}
summary(dHCP$mother_alcoholyn.enrolment_1)
```

```{r}
summary(dHCP$mother_bmi.enrolment_1)
```

```{r}
summary(dHCP$mother_smoking.enrolment_1)
```

```{r}
summary(dHCP$baby_ga_at_birth_weeks.baby_born_1)
```

```{r}
dHCP$baby_ga_at_birth_weeks.baby_born_1[dHCP$baby_ga_at_birth_weeks.baby_born_1==49.00] <- NA 
```
One GA at birth was entered incorrectly. Removed after speaking to database manager. 

```{r}
summary(dHCP$baby_ga_at_birth_weeks.baby_born_1)
```
Max is now 43.57. Fine (checked with database manager

```{r}
summary(dHCP$baby_gender.baby_born_1)
```


```{r}
summary(dHCP$fscan_ga_at_scan_weeks.fetal_scan_1)
```
The max value is 83.71 which is wrong. Checked with database manager and removed those with GA at scan over 45

```{r}
dHCP$fscan_ga_at_scan_weeks.fetal_scan_1[dHCP$fscan_ga_at_scan_weeks.fetal_scan_1>=45] <- NA 
```

```{r}
summary(dHCP$fscan_ga_at_scan_weeks.fetal_scan_1)
```

```{r}
summary(dHCP$fscan_ga_at_scan_weeks.fetal_scan_arm_2)
```

```{r}
summary(dHCP$nscan_ga_at_scan_weeks.neonatal_scan_1)
```

```{r}
summary(dHCP$nscan_ga_at_scan_weeks.neonatal_scan_arm_2)
```

```{r}
summary(dHCP$F_EPDSTotal)
```

```{r}
summary(dHCP$F2_EPDSTotal)
```

```{r}
summary(dHCP$N_EPDSTotal)
```


```{r}
summary(dHCP$N2_EPDSTotal)
```

Changing variable type where needed
```{r}
dHCP$participantID <- as.character(dHCP$participantID)
dHCP$ANY_OTHER <- as.character(dHCP$ANY_OTHER)
dHCP$PREG_OTHER <- as.character(dHCP$PREG_OTHER)
dHCP$mother_occupation.enrolment_1 <- as.character(dHCP$mother_occupation.enrolment_1)
```

```{r}
EPDS_HOW_MANY <- subset(dHCP, select=c(F_EPDSTotal,N_EPDSTotal,F2_EPDSTotal,N2_EPDSTotal))
str(EPDS_HOW_MANY)
```

Now removing empty cells and checking again number of participants
```{r}
EPDS_HOW_MANY2 <- janitor::remove_empty(EPDS_HOW_MANY, which = "rows")  
str(EPDS_HOW_MANY2)
```

## Subsetting into smaller databases 

After this, we subsetted the main database into the smaller ones used for the analyses above
```{r}
F1_DF <- subset(dHCP, select=c(participantID,ANY_DEPR, PREG_DEPR, ANY_ANX, PREG_ANX, ANY_OTHER,
                               PREG_OTHER,ANY_ANTIDEP,PREG_ANTIDEP,ANY_THER,PREG_THER, 
                               OVERALL_MoodOrAnx,OVERALL_AnyMH, Higest_F_EPDS, Highest_N_EPDS, 
                               Highest_Perinatal_EPDS, mother_ethnicity.enrolment_1, 
                               mother_age.enrolment_1, mother_education.enrolment_1, 
                               mother_occupation.enrolment_1, 
                               mother_smokingyn.enrolment_1, mother_alcoholyn.enrolment_1,
                               mother_bmi.enrolment_1, mother_smoking.enrolment_1,
                               baby_ga_at_birth_weeks.baby_born_1, baby_gender.baby_born_1,
                               fscan_ga_at_scan_weeks.fetal_scan_1,
                               scan_completed.neonatal_scan_1,
                               scan_completed.neonatal_scan_arm_2,fscan1_completed.fetal_scan_1,
                               fscan1_completed.fetal_scan_arm_2, F_EPDSQ1, F_EPDSQ2, F_EPDSQ3, F_EPDSQ4, 
                               F_EPDSQ5, F_EPDSQ6, F_EPDSQ7,
                               F_EPDSQ8, F_EPDSQ9, F_EPDSQ10, F_EPDSTotal, MQ_EverTreated, 
                               MQ_EverUnderPsych, MQ_EverAdmitted, MQ_HistoryBunch))
                               
F2_DF <- subset(dHCP, select=c(participantID,ANY_DEPR,PREG_DEPR, ANY_ANX,
                               PREG_ANX,ANY_OTHER,PREG_OTHER,ANY_ANTIDEP,PREG_ANTIDEP,ANY_THER,
                               PREG_THER, OVERALL_MoodOrAnx,OVERALL_AnyMH,Higest_F_EPDS,
                               Highest_N_EPDS,
                               Highest_Perinatal_EPDS,mother_ethnicity.enrolment_1,
                               mother_age.enrolment_1, mother_education.enrolment_1, 
                               mother_occupation.enrolment_1,
                               mother_smokingyn.enrolment_1, mother_alcoholyn.enrolment_1, 
                               mother_bmi.enrolment_1, mother_smoking.enrolment_1,
                               baby_ga_at_birth_weeks.baby_born_1,
                               baby_gender.baby_born_1,fscan_ga_at_scan_weeks.fetal_scan_arm_2, 
                               scan_completed.neonatal_scan_1, scan_completed.neonatal_scan_arm_2,
                               fscan1_completed.fetal_scan_1, 
                               fscan1_completed.fetal_scan_arm_2,F2_EPDSQ1, F2_EPDSQ2, F2_EPDSQ3,
                               F2_EPDSQ4, F2_EPDSQ5, F2_EPDSQ6, F2_EPDSQ7,
                               F2_EPDSQ8, F2_EPDSQ9, F2_EPDSQ10, F2_EPDSTotal, MQ_EverTreated, 
                               MQ_EverUnderPsych, MQ_EverAdmitted, MQ_HistoryBunch))

N1_DF <- subset(dHCP, select=c(participantID,ANY_DEPR,PREG_DEPR, ANY_ANX,
                               PREG_ANX,ANY_OTHER,PREG_OTHER,ANY_ANTIDEP,PREG_ANTIDEP,
                               ANY_THER,
                               PREG_THER, OVERALL_MoodOrAnx,OVERALL_AnyMH,Higest_F_EPDS,
                               Highest_N_EPDS,
                               Highest_Perinatal_EPDS,mother_ethnicity.enrolment_1,
                               mother_age.enrolment_1, mother_education.enrolment_1, 
                               mother_occupation.enrolment_1,
                               mother_smokingyn.enrolment_1, mother_alcoholyn.enrolment_1,
                               mother_bmi.enrolment_1, mother_smoking.enrolment_1,
                               baby_ga_at_birth_weeks.baby_born_1,
                               baby_gender.baby_born_1,nscan_ga_at_scan_weeks.neonatal_scan_1, 
                               scan_completed.neonatal_scan_1,
                               scan_completed.neonatal_scan_arm_2,fscan1_completed.fetal_scan_1,
                               fscan1_completed.fetal_scan_arm_2,N_EPDSQ1, N_EPDSQ2, N_EPDSQ3, N_EPDSQ4,
                               N_EPDSQ5,N_EPDSQ6, N_EPDSQ7,
                               N_EPDSQ8, N_EPDSQ9, N_EPDSQ10, N_EPDSTotal, MQ_EverTreated,
                               MQ_EverUnderPsych, MQ_EverAdmitted, MQ_HistoryBunch))

N2_DF <- subset(dHCP, select=c(participantID,ANY_DEPR,PREG_DEPR, ANY_ANX, PREG_ANX,ANY_OTHER,PREG_OTHER,ANY_ANTIDEP,PREG_ANTIDEP,ANY_THER,
                               PREG_THER, OVERALL_MoodOrAnx,OVERALL_AnyMH,Higest_F_EPDS,
                               Highest_N_EPDS,
                               Highest_Perinatal_EPDS, mother_ethnicity.enrolment_1,
                               mother_age.enrolment_1, mother_education.enrolment_1, 
                               mother_occupation.enrolment_1,
                               mother_smokingyn.enrolment_1, mother_alcoholyn.enrolment_1, 
                               mother_bmi.enrolment_1, mother_smoking.enrolment_1,
                               baby_ga_at_birth_weeks.baby_born_1, baby_gender.baby_born_1, nscan_ga_at_scan_weeks.neonatal_scan_arm_2, 
                               scan_completed.neonatal_scan_1, scan_completed.neonatal_scan_arm_2,fscan1_completed.fetal_scan_1,
                               fscan1_completed.fetal_scan_arm_2, N2_EPDSQ1, N2_EPDSQ2, N2_EPDSQ3,
                               N2_EPDSQ4, N2_EPDSQ5,N2_EPDSQ6, N2_EPDSQ7,
                               N2_EPDSQ8, N2_EPDSQ9, N2_EPDSQ10, N2_EPDSTotal, MQ_EverTreated, 
                               MQ_EverUnderPsych, MQ_EverAdmitted, MQ_HistoryBunch))
```


```{r results='hide'}
F1_DF_Clean <- F1_DF %>% drop_na(F_EPDSTotal)
str(F1_DF_Clean)
```

```{r results='hide'}
N1_DF_Clean <- N1_DF %>% drop_na(N_EPDSTotal)
str(N1_DF_Clean)
```

```{r results='hide'}
F2_DF_Clean <- F2_DF %>% drop_na(F2_EPDSTotal)
str(F2_DF_Clean)
```

```{r results='hide'}
N2_DF_Clean <- N2_DF %>% drop_na(N2_EPDSTotal)
str(N2_DF_Clean)
```

Descriptives EPDS
```{r}
psych::describe(F1_DF_Clean$F_EPDSTotal)
```

```{r}
psych::describe(N1_DF_Clean$N_EPDSTotal)
```

```{r}
psych::describe(F2_DF_Clean$F2_EPDSTotal)
```

```{r}
psych::describe(N2_DF_Clean$N2_EPDSTotal)
```

Calculating how many participants had a score of 11 or more
```{r}
sum(F1_DF_Clean$F_EPDSTotal>10, na.rm=TRUE)
```

```{r}
sum(N1_DF_Clean$N_EPDSTotal>10, na.rm=TRUE)
```

```{r}
sum(F2_DF_Clean$F2_EPDSTotal>10, na.rm=TRUE)
```

```{r}
sum(N2_DF_Clean$N2_EPDSTotal>10, na.rm=TRUE)
```

Calculating how many participants had a score of 13 or more

```{r}
sum(F1_DF_Clean$F_EPDSTotal>12, na.rm=TRUE)
```

```{r}
sum(N1_DF_Clean$N_EPDSTotal>12, na.rm=TRUE)
```

```{r}
sum(F2_DF_Clean$F2_EPDSTotal>12, na.rm=TRUE)
```

```{r}
sum(N2_DF_Clean$N2_EPDSTotal>12, na.rm=TRUE)
```

Descriptives for maternal age at EPDS time 

```{r}
psych::describe(F1_DF_Clean$mother_age.enrolment_1)
```

```{r}
psych::describe(F2_DF_Clean$mother_age.enrolment_1)
```

```{r}
psych::describe(N1_DF_Clean$mother_age.enrolment_1)
```

```{r}
psych::describe(N2_DF_Clean$mother_age.enrolment_1)
```

Descriptives for baby age at EPDS time 
```{r}
psych::describe(F1_DF_Clean$fscan_ga_at_scan_weeks.fetal_scan_1)
```

```{r}
psych::describe(F2_DF_Clean$fscan_ga_at_scan_weeks.fetal_scan_arm_2)
```

```{r}
psych::describe(N1_DF_Clean$nscan_ga_at_scan_weeks.neonatal_scan_1)
```

```{r}
psych::describe(N2_DF_Clean$nscan_ga_at_scan_weeks.neonatal_scan_arm_2)
```

Descriptives for baby age at birth
```{r}
psych::describe(F1_DF_Clean$baby_ga_at_birth_weeks.baby_born_1)
```

```{r}
psych::describe(F2_DF_Clean$baby_ga_at_birth_weeks.baby_born_1)
```

```{r}
psych::describe(N1_DF_Clean$baby_ga_at_birth_weeks.baby_born_1)
```

```{r}
psych::describe(N2_DF_Clean$baby_ga_at_birth_weeks.baby_born_1)
```

Descriptives for BMI 
```{r}
psych::describe(F1_DF_Clean$mother_bmi.enrolment_1)
```

```{r}
psych::describe(F2_DF_Clean$mother_bmi.enrolment_1)
```

```{r}
psych::describe(N1_DF_Clean$mother_bmi.enrolment_1)
```

```{r}
psych::describe(N2_DF_Clean$mother_bmi.enrolment_1)
```

What other mental health conditions
```{r}
F1_DF_Clean$ANY_OTHER <- as.factor(F1_DF_Clean$ANY_OTHER)
summary(F1_DF_Clean$ANY_OTHER)
```

History of mental health describe
```{r}
summary(F1_DF_Clean$OVERALL_AnyMH)
summary(F2_DF_Clean$OVERALL_AnyMH)
summary(N1_DF_Clean$OVERALL_AnyMH)
summary(N2_DF_Clean$OVERALL_AnyMH)
```

```{r}
summary(F1_DF_Clean$ANY_DEPR)
summary(F2_DF_Clean$ANY_DEPR)
summary(N1_DF_Clean$ANY_DEPR)
summary(N2_DF_Clean$ANY_DEPR)
```

```{r}
summary(F1_DF_Clean$ANY_ANX)
summary(F2_DF_Clean$ANY_ANX)
summary(N1_DF_Clean$ANY_ANX)
summary(N2_DF_Clean$ANY_ANX)
```

## Plots

## Calculating EPDS 3A 

```{r}
F1_DF_Clean$F_EPDS3A = F1_DF_Clean$F_EPDSQ3 + F1_DF_Clean$F_EPDSQ4 + F1_DF_Clean$F_EPDSQ5 
psych::describe(F1_DF_Clean$F_EPDS3A)
```

```{r}
N1_DF_Clean$N_EPDS3A = N1_DF_Clean$N_EPDSQ3 + N1_DF_Clean$N_EPDSQ4 + N1_DF_Clean$N_EPDSQ5 
psych::describe(N1_DF_Clean$N_EPDS3A)
```

## More descriptives

```{r}
summary(F1_DF_Clean$MQ_EverTreated)
summary(F1_DF_Clean$MQ_EverUnderPsych)
summary(F1_DF_Clean$MQ_EverAdmitted)
summary(F1_DF_Clean$MQ_HistoryBunch)
```

```{r}
summary(F2_DF_Clean$MQ_EverTreated)
summary(F2_DF_Clean$MQ_EverUnderPsych)
summary(F2_DF_Clean$MQ_EverAdmitted)
summary(F2_DF_Clean$MQ_HistoryBunch)
```

```{r}
summary(N1_DF_Clean$MQ_EverTreated)
summary(N1_DF_Clean$MQ_EverUnderPsych)
summary(N1_DF_Clean$MQ_EverAdmitted)
summary(N1_DF_Clean$MQ_HistoryBunch)
```

```{r}
summary(N2_DF_Clean$MQ_EverTreated)
summary(N2_DF_Clean$MQ_EverUnderPsych)
summary(N2_DF_Clean$MQ_EverAdmitted)
summary(N2_DF_Clean$MQ_HistoryBunch)
```

```{r}
summary(F1_DF_Clean$mother_ethnicity.enrolment_1)
```

```{r}
summary(N1_DF_Clean$mother_ethnicity.enrolment_1)
```

```{r}
summary(F2_DF_Clean$mother_ethnicity.enrolment_1)
```

```{r}
summary(N2_DF_Clean$mother_ethnicity.enrolment_1)
```

## EPDS and history of mental health
```{r}
F1_dHCP$NoMH = F1_dHCP$OVERALL_AnyMH =="No"
F1_dHCP$YesMH = F1_dHCP$OVERALL_AnyMH =="Yes"
summary(F1_dHCP$NoMH)
summary(F1_dHCP$YesMH)
```

```{r}
by(F1_dHCP$Higest_F_EPDS, F1_dHCP$OVERALL_AnyMH, stat.desc, basic = FALSE, norm =TRUE)
```

```{r}
Highest_F_EPDS_NoMH = F1_dHCP$Higest_F_EPDS[F1_dHCP$OVERALL_AnyMH=="No"]
Highest_F_EPDS_YesMH = F1_dHCP$Higest_F_EPDS[F1_dHCP$OVERALL_AnyMH=="Yes"]
plotNormalHistogram(Highest_F_EPDS_NoMH)
plotNormalHistogram(Highest_F_EPDS_NoMH)
```

```{r}
wilcox.test( formula = Higest_F_EPDS~OVERALL_AnyMH, data=F1_dHCP)
```

```{r}
library(effsize)
VD.A(d=F1_dHCP$Higest_F_EPDS,
     f=F1_dHCP$OVERALL_AnyMH)
```

```{r}
N1_dHCP$NoMH = N1_dHCP$OVERALL_AnyMH =="No"
N1_dHCP$YesMH = N1_dHCP$OVERALL_AnyMH =="Yes"
summary(N1_dHCP$NoMH)
summary(N1_dHCP$YesMH)
```

```{r}
by(N1_dHCP$Highest_N_EPDS, N1_dHCP$OVERALL_AnyMH, stat.desc, basic = FALSE, norm =TRUE)
```

```{r}
Highest_N_EPDS_NoMH = N1_dHCP$Highest_N_EPDS[N1_dHCP$OVERALL_AnyMH=="No"]
Highest_N_EPDS_YesMH = N1_dHCP$Highest_N_EPDS[N1_dHCP$OVERALL_AnyMH=="Yes"]
plotNormalHistogram(Highest_N_EPDS_NoMH)
plotNormalHistogram(Highest_N_EPDS_NoMH)
```

```{r}
wilcox.test( formula = Highest_N_EPDS~OVERALL_AnyMH, data=N1_dHCP)
```

```{r}
library(effsize)
VD.A(d=N1_dHCP$Highest_N_EPDS,
     f=N1_dHCP$OVERALL_AnyMH)
```

### Plotting the highest fetal and neonatal EPDS scores against history 
```{r fig.show='hide' , warning=FALSE}
p13 <- ggplot(F1_dHCP, aes(x=OVERALL_AnyMH, y=Higest_F_EPDS, fill=OVERALL_AnyMH))+
  geom_violin(trim=TRUE)+labs(x="Mental health history", y="Highest Prenatal EPDS")+ylim(0,30)
p13a<- p13 + geom_boxplot(width=0.1, fill="white")+scale_fill_manual(values=c("#189ba0", "#a64264")) +
  theme(legend.position="none", text=element_text(size=15))
p13a
```

```{r fig.show='hide' , warning=FALSE}
p14 <- ggplot(N1_dHCP, aes(x=OVERALL_AnyMH, y=Highest_N_EPDS, fill=OVERALL_AnyMH))+
  geom_violin(trim=TRUE)+labs(x="Mental health history", y="Highest Postnatal EPDS")+ylim(0,30)
p14a<- p14 + geom_boxplot(width=0.1, fill="white")+scale_fill_manual(values=c("#189ba0", "#a64264"))+
theme(legend.position="none", text=element_text(size=15)) 
p14a
```

```{r warning=FALSE}
grid14a <- plot_grid(p13a, p14a)
grid14a
```


## More descriptives for EPDS 3A 

For the timepoints that were not done above
```{r}
F2_DF_Clean$F_EPDS3A = F2_DF_Clean$F2_EPDSQ3 + F2_DF_Clean$F2_EPDSQ4 + F2_DF_Clean$F2_EPDSQ5 
psych::describe(F2_DF_Clean$F_EPDS3A)
```

```{r}
N2_DF_Clean$N_EPDS3A = N2_DF_Clean$N2_EPDSQ3 + N2_DF_Clean$N2_EPDSQ4 + N2_DF_Clean$N2_EPDSQ5 
psych::describe(N2_DF_Clean$N_EPDS3A)
```

How many EPDS 3A scores over threshold 
```{r}
sum(F1_DF_Clean$F_EPDS3A>3, na.rm=TRUE)
sum(F2_DF_Clean$F_EPDS3A>3, na.rm=TRUE)
sum(N1_DF_Clean$N_EPDS3A>3, na.rm=TRUE)
sum(N2_DF_Clean$N_EPDS3A>3, na.rm=TRUE)
```

```{r}
sum(F1_DF_Clean$F_EPDS3A>5, na.rm=TRUE)
sum(F2_DF_Clean$F_EPDS3A>5, na.rm=TRUE)
sum(N1_DF_Clean$N_EPDS3A>5, na.rm=TRUE)
sum(N2_DF_Clean$N_EPDS3A>5, na.rm=TRUE)
```

How many would have been missed
```{r}
length(F1_DF_Clean$participantID[F1_DF_Clean$F_EPDS3A>3 & F1_DF_Clean$F_EPDSTotal<11])
length(F1_DF_Clean$participantID[F1_DF_Clean$F_EPDS3A>5 & F1_DF_Clean$F_EPDSTotal<11])
```

```{r}
length(N1_DF_Clean$participantID[N1_DF_Clean$N_EPDS3A>3 & N1_DF_Clean$N_EPDSTotal<11])
length(N1_DF_Clean$participantID[N1_DF_Clean$N_EPDS3A>5 & N1_DF_Clean$N_EPDSTotal<11])
```

How about if using 13 or more as cutoff 
```{r}
length(F1_DF_Clean$participantID[F1_DF_Clean$F_EPDS3A>3 & F1_DF_Clean$F_EPDSTotal<13])
length(F1_DF_Clean$participantID[F1_DF_Clean$F_EPDS3A>5 & F1_DF_Clean$F_EPDSTotal<13])
```

```{r}
length(N1_DF_Clean$participantID[N1_DF_Clean$N_EPDS3A>3 & N1_DF_Clean$N_EPDSTotal<13])
length(N1_DF_Clean$participantID[N1_DF_Clean$N_EPDS3A>5 & N1_DF_Clean$N_EPDSTotal<13])
```

```{r}
str(F1_DF_Clean$OVERALL_AnyMH)
```





How much do anxiety and depression overlap 
```{r}
length(F1_DF_Clean$participantID[F1_DF_Clean$OVERALL_AnyMH=="No"])
length(F1_DF_Clean$participantID[F1_DF_Clean$ANY_DEPR=="Yes" & F1_DF_Clean$ANY_ANX=="Yes"])
length(F1_DF_Clean$participantID[F1_DF_Clean$ANY_DEPR=="Yes" & F1_DF_Clean$ANY_ANX=="No"])
length(F1_DF_Clean$participantID[F1_DF_Clean$ANY_DEPR=="No" & F1_DF_Clean$ANY_ANX=="Yes"])
```

```{r}
length(N1_DF_Clean$participantID[N1_DF_Clean$OVERALL_AnyMH=="No"])
length(N1_DF_Clean$participantID[N1_DF_Clean$ANY_DEPR=="Yes" & N1_DF_Clean$ANY_ANX=="Yes"])
length(N1_DF_Clean$participantID[N1_DF_Clean$ANY_DEPR=="Yes" & N1_DF_Clean$ANY_ANX=="No"])
length(N1_DF_Clean$participantID[N1_DF_Clean$ANY_DEPR=="No" & N1_DF_Clean$ANY_ANX=="Yes"])
```

Highest EPDS 3A

Fetal 
```{r}
Highest_EPDS3A_Fetal <-read.csv("Highest_EPDS3A_Fetal.csv", header=TRUE, na.strings=c("","NA", " ", "not known"))
```

Descriptives for each group 
```{r}
by(Highest_EPDS3A_Fetal$HF_EPDS3A, Highest_EPDS3A_Fetal$ANY_ANX, stat.desc, basic = FALSE, norm =TRUE)
```

```{r}
wilcox.test( formula = HF_EPDS3A~ANY_ANX, data=Highest_EPDS3A_Fetal)
```

Calculating effect size
```{r}
VD.A(d=Highest_EPDS3A_Fetal$HF_EPDS3A,
     f=Highest_EPDS3A_Fetal$ANY_ANX)
```

```{r fig.show='hide' , warning=FALSE}
p20 <- ggplot(Highest_EPDS3A_Fetal, aes(x=ANY_ANX, y=HF_EPDS3A, fill=ANY_ANX))+
  geom_violin(trim=TRUE)+ylim(0,9)+labs(x="Anxiety history", y="Highest Prenatal EPDS 3A")
p20a<- p20 + geom_boxplot(width=0.1, fill="white")+scale_fill_manual(values=c("#189ba0", "#a64264"))+
  theme(legend.position="none",text=element_text(size=15))+ scale_y_continuous(breaks=c(0,3,6,9))
p20a
```

Neonatal
```{r}
Highest_EPDS3A_Neonatal <-read.csv("Highest_EPDS3A_Neonatal.csv", header=TRUE,
                                   na.strings=c("","NA", " ", "not known"))
```

Descriptives for each group 
```{r}
by(Highest_EPDS3A_Neonatal$HN_EPDS3A, Highest_EPDS3A_Neonatal$ANY_ANX, stat.desc, basic = FALSE, 
   norm =TRUE)
```

```{r}
wilcox.test( formula = HN_EPDS3A~ANY_ANX, data=Highest_EPDS3A_Neonatal)
```

Calculating effect size
```{r}
VD.A(d=Highest_EPDS3A_Neonatal$HN_EPDS3A,
     f=Highest_EPDS3A_Neonatal$ANY_ANX)
```


[[EXTRA ANALYSIS FOLLOWING PEER REVIEW]]
Now try the same but for history of depression and history of anxiety 

How many participants with depression, how many with anxiety, how many with both 

For prenatal 
```{r}
F1_dHCP <-F1_dHCP %>%
    mutate(MentalHealthCat = case_when(
      ANY_DEPR=="Yes" & ANY_ANX=="No" ~ 0,
      ANY_DEPR=="No" & ANY_ANX=="Yes" ~ 1,
      ANY_DEPR=="Yes" & ANY_ANX=="Yes" ~ 2, 
      ANY_DEPR=="No" & ANY_ANX=="No" ~ 3, 
      TRUE ~ NA_real_
    )) 
```

```{r}
F1_dHCP$MentalHealthCat2 <- factor(F1_dHCP$MentalHealthCat, levels=c(0,1,2,3), 
                                   labels=c("Depression only", "Anxiety only", "Both", "Neither"))
summary(F1_dHCP$MentalHealthCat2)
```



```{r}
group_by(F1_dHCP, MentalHealthCat2) %>%
  summarise(
    count = n(),
    mean = mean(Higest_F_EPDS, na.rm = TRUE),
    sd = sd(Higest_F_EPDS, na.rm = TRUE)
  )
```

For postnatal 
```{r}
N1_dHCP <-N1_dHCP %>%
    mutate(MentalHealthCat = case_when(
      ANY_DEPR=="Yes" & ANY_ANX=="No" ~ 0,
      ANY_DEPR=="No" & ANY_ANX=="Yes" ~ 1,
      ANY_DEPR=="Yes" & ANY_ANX=="Yes" ~ 2, 
      ANY_DEPR=="No" & ANY_ANX=="No" ~ 3, 
      TRUE ~ NA_real_
    )) 
```

```{r}
N1_dHCP$MentalHealthCat2 <- factor(N1_dHCP$MentalHealthCat, levels=c(0,1,2,3), 
                                   labels=c("Depression only", "Anxiety only", "Both", "Neither"))
summary(N1_dHCP$MentalHealthCat2)
```


```{r}
group_by(N1_dHCP, MentalHealthCat2) %>%
  summarise(
    count = n(),
    mean = mean(Highest_N_EPDS, na.rm = TRUE),
    sd = sd(Highest_N_EPDS, na.rm = TRUE)
  )
```



For EPDS 3A fetal comparing groups 

```{r}
Highest_EPDS3A_Fetal <-Highest_EPDS3A_Fetal %>%
    mutate(MentalHealthCat = case_when(
      ANY_DEPR=="Yes" & ANY_ANX=="No" ~ 0,
      ANY_DEPR=="No" & ANY_ANX=="Yes" ~ 1,
      ANY_DEPR=="Yes" & ANY_ANX=="Yes" ~ 2, 
      ANY_DEPR=="No" & ANY_ANX=="No" ~ 3, 
      TRUE ~ NA_real_
    )) 
```

```{r}
Highest_EPDS3A_Fetal$MentalHealthCat2 <- factor(Highest_EPDS3A_Fetal$MentalHealthCat, levels=c(0,1,2,3), labels=c("Depression only", "Anxiety only", "Both", "Neither"))
summary(Highest_EPDS3A_Fetal$MentalHealthCat2)
```


```{r}
group_by(Highest_EPDS3A_Fetal, MentalHealthCat2) %>%
  summarise(
    count = n(),
    mean = mean(HF_EPDS3A, na.rm = TRUE),
    sd = sd(HF_EPDS3A, na.rm = TRUE)
  )
```


For EPDS 3A neonatal comparing groups 

```{r}
Highest_EPDS3A_Neonatal <-Highest_EPDS3A_Neonatal %>%
    mutate(MentalHealthCat = case_when(
      ANY_DEPR=="Yes" & ANY_ANX=="No" ~ 0,
      ANY_DEPR=="No" & ANY_ANX=="Yes" ~ 1,
      ANY_DEPR=="Yes" & ANY_ANX=="Yes" ~ 2, 
      ANY_DEPR=="No" & ANY_ANX=="No" ~ 3, 
      TRUE ~ NA_real_
    )) 
```

```{r}
Highest_EPDS3A_Neonatal$MentalHealthCat2 <- factor(Highest_EPDS3A_Neonatal$MentalHealthCat, 
                                                   levels=c(0,1,2,3), labels=c("Depression only", 
                                                                               "Anxiety only", "Both", 
                                                                               "Neither"))
summary(Highest_EPDS3A_Neonatal$MentalHealthCat2)
```


```{r}
group_by(Highest_EPDS3A_Neonatal, MentalHealthCat2) %>%
  summarise(
    count = n(),
    mean = mean(HN_EPDS3A, na.rm = TRUE),
    sd = sd(HN_EPDS3A, na.rm = TRUE)
  )
```


## Initial descriptives and setup (overall sample)
```{r}
OverallEFA9 <-read.csv("OverallEFA9.csv", header=TRUE, na.strings=c("","NA", " ", "not known"))
OverallEFAClean9 <- janitor::remove_empty(OverallEFA9, which = "cols") 
```

```{r results="hide", warning=FALSE, comment=FALSE, message=FALSE}
((plyr::count(OverallEFAClean9$O_EPDS1))*100)/1190
((plyr::count(OverallEFAClean9$O_EPDS2))*100)/1190
((plyr::count(OverallEFAClean9$O_EPDS3))*100)/1190
((plyr::count(OverallEFAClean9$O_EPDS4))*100)/1190
((plyr::count(OverallEFAClean9$O_EPDS5))*100)/1190
((plyr::count(OverallEFAClean9$O_EPDS6))*100)/1190
((plyr::count(OverallEFAClean9$O_EPDS7))*100)/1190
((plyr::count(OverallEFAClean9$O_EPDS8))*100)/1190
((plyr::count(OverallEFAClean9$O_EPDS9))*100)/1190
((plyr::count(OverallEFAClean9$O_EPDS10))*100)/1190
```

Calculating Cronbach's alpha
```{r results="hide"}
psych::alpha(OverallEFAClean9)
```

Calculating McDonald's alpha 
```{r}
ci.reliability(OverallEFAClean9, type="omega")
```



Try different figures https://wellcomeopenresearch.org/articles/4-63
```{r}
library(gghalves)
library(PupillometryR)
```


```{r warning=FALSE}
Raincloud1 <- ggplot(Highest_EPDS3A_Fetal,aes(x=ANY_ANX,y=HF_EPDS3A, fill = ANY_ANX, colour=ANY_ANX))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =1)+
  geom_point(position = position_jitter(width = .2), size = .2)+
  geom_boxplot(aes(x = as.numeric(ANY_ANX)+0.25, y =HF_EPDS3A),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + ylab('Highest Prenatal EPDS-3A')+xlab('Anxiety history')+theme_cowplot()+guides(fill = FALSE, colour = FALSE)+ scale_y_continuous(breaks=c(0,3,6,9),limits=c(0,9),oob = scales::squish)+scale_fill_manual(values=c("#189ba0", "#a64264"))+scale_colour_manual(values=c("#189ba0", "#a64264"))+theme(legend.position="none",text=element_text(size=15))
Raincloud1
```

```{r warning=FALSE}

Raincloud2 <- ggplot(Highest_EPDS3A_Neonatal,aes(x=ANY_ANX,y=HN_EPDS3A, fill = ANY_ANX, colour=ANY_ANX))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =1)+
  geom_point(position = position_jitter(width = .2), size = .2)+
  geom_boxplot(aes(x = as.numeric(ANY_ANX)+0.25, y =HN_EPDS3A),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + ylab('Highest Postnatal EPDS-3A')+xlab('Anxiety history')+theme_cowplot()+guides(fill = FALSE, colour = FALSE)+ scale_y_continuous(breaks=c(0,3,6,9),limits=c(0,9),oob = scales::squish)+scale_fill_manual(values=c("#189ba0", "#a64264"))+scale_colour_manual(values=c("#189ba0", "#a64264"))+theme(legend.position="none",text=element_text(size=15))
Raincloud2
```

```{r warning=FALSE}
RainFig2 <- plot_grid(Raincloud1, Raincloud2)
RainFig2
```



```{r warning=FALSE}
Raincloud3 <- ggplot(F1_dHCP,aes(x=OVERALL_AnyMH,y=Higest_F_EPDS, fill = OVERALL_AnyMH, colour=OVERALL_AnyMH))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =1)+
  geom_point(position = position_jitter(width = .2), size = .2)+
  geom_boxplot(aes(x = as.numeric(OVERALL_AnyMH)+0.25, y =Higest_F_EPDS),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + ylab('Highest Prenatal EPDS')+xlab('Poor mental health history')+theme_cowplot()+guides(fill = FALSE, colour = FALSE)+ scale_y_continuous(breaks=c(0,10,20,30),limits=c(0,30),oob = scales::squish)+scale_fill_manual(values=c("#189ba0", "#a64264"))+scale_colour_manual(values=c("#189ba0", "#a64264"))+theme(legend.position="none",text=element_text(size=15))
Raincloud3
```




```{r warning=FALSE}
Raincloud4 <- ggplot(N1_dHCP,aes(x=OVERALL_AnyMH,y=Highest_N_EPDS, fill = OVERALL_AnyMH, colour=OVERALL_AnyMH))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =1)+
  geom_point(position = position_jitter(width = .2), size = .2)+
  geom_boxplot(aes(x = as.numeric(OVERALL_AnyMH)+0.25, y =Highest_N_EPDS),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + ylab('Highest Postnatal EPDS')+xlab('Poor mental health history')+theme_cowplot()+guides(fill = FALSE, colour = FALSE)+ scale_y_continuous(breaks=c(0,10,20,30),limits=c(0,30),oob = scales::squish)+scale_fill_manual(values=c("#189ba0", "#a64264"))+scale_colour_manual(values=c("#189ba0", "#a64264"))+theme(legend.position="none",text=element_text(size=15))
Raincloud4
```

```{r warning=FALSE}
RainFig1 <- plot_grid(Raincloud3, Raincloud4)
RainFig1
```

Plots for Supplement 


```{r warning=FALSE}
RaincloudSup1 <- ggplot(F1_dHCP,aes(x=MentalHealthCat2,y=Higest_F_EPDS, fill = MentalHealthCat2, colour=MentalHealthCat2))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =1)+
  geom_point(position = position_jitter(width = .2), size = .2)+
  geom_boxplot(aes(x = as.numeric(MentalHealthCat2)+0.25, y =Higest_F_EPDS),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + ylab('Highest Prenatal EPDS')+xlab('Poor mental health history')+theme_cowplot()+guides(fill = FALSE, colour = FALSE)+ scale_y_continuous(breaks=c(0,10,20,30),limits=c(0,30),oob = scales::squish)+scale_fill_manual(values=c("#189ba0", "#73c1c4", "#a64264", "#830442"))+scale_colour_manual(values=c("#189ba0", "#73c1c4", "#a64264", "#830442"))+theme(legend.position="none",text=element_text(size=15))
RaincloudSup1
```

```{r warning=FALSE}
RaincloudSup2 <- ggplot(N1_dHCP,aes(x=MentalHealthCat2,y=Highest_N_EPDS, fill = MentalHealthCat2, colour=MentalHealthCat2))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =1)+
  geom_point(position = position_jitter(width = .2), size = .2)+
  geom_boxplot(aes(x = as.numeric(MentalHealthCat2)+0.25, y =Higest_F_EPDS),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + ylab('Highest Postnatal EPDS')+xlab('Poor mental health history')+theme_cowplot()+guides(fill = FALSE, colour = FALSE)+ scale_y_continuous(breaks=c(0,10,20,30),limits=c(0,30),oob = scales::squish)+scale_fill_manual(values=c("#189ba0", "#73c1c4", "#a64264", "#830442"))+scale_colour_manual(values=c("#189ba0", "#73c1c4", "#a64264", "#830442"))+theme(legend.position="none",text=element_text(size=15))
RaincloudSup2
```

```{r warning=FALSE}
RaincloudSup3 <- ggplot(Highest_EPDS3A_Fetal,aes(x=MentalHealthCat2,y=HF_EPDS3A, fill = MentalHealthCat2, colour=MentalHealthCat2))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =1)+
  geom_point(position = position_jitter(width = .2), size = .2)+
  geom_boxplot(aes(x = as.numeric(MentalHealthCat2)+0.25, y =HF_EPDS3A),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + ylab('Highest Prenatal EPDS-3A')+xlab('Poor mental health history')+theme_cowplot()+guides(fill = FALSE, colour = FALSE)+ scale_y_continuous(breaks=c(0,3,6,9),limits=c(0,9),oob = scales::squish)+scale_fill_manual(values=c("#189ba0", "#73c1c4", "#a64264", "#830442"))+scale_colour_manual(values=c("#189ba0", "#73c1c4", "#a64264", "#830442"))+theme(legend.position="none",text=element_text(size=15))
RaincloudSup3
```

```{r warning=FALSE}
RaincloudSup4 <- ggplot(Highest_EPDS3A_Neonatal,aes(x=MentalHealthCat2,y=HN_EPDS3A, fill = MentalHealthCat2, colour=MentalHealthCat2))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =1)+
  geom_point(position = position_jitter(width = .2), size = .2)+
  geom_boxplot(aes(x = as.numeric(MentalHealthCat2)+0.25, y =HN_EPDS3A),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + ylab('Highest Postnatal EPDS-3A')+xlab('Poor mental health history')+theme_cowplot()+guides(fill = FALSE, colour = FALSE)+ scale_y_continuous(breaks=c(0,3,6,9),limits=c(0,9),oob = scales::squish)+scale_fill_manual(values=c("#189ba0", "#73c1c4", "#a64264", "#830442"))+scale_colour_manual(values=c("#189ba0", "#73c1c4", "#a64264", "#830442"))+theme(legend.position="none",text=element_text(size=15))
RaincloudSup4
```


Extra info 
How many have history of poor mental health and score 11 or more on EPDS 
```{r}
length(F1_dHCP$participantID[F1_dHCP$OVERALL_AnyMH=="Yes" & F1_dHCP$Higest_F_EPDS>10])
```

```{r}
length(F1_DF_Clean$participantID[F1_DF_Clean$OVERALL_AnyMH=="Yes" & F1_DF_Clean$Higest_F_EPDS<11])
```

```{r}
length(F1_DF_Clean$participantID[F1_DF_Clean$OVERALL_AnyMH=="No" & F1_DF_Clean$Higest_F_EPDS>10])
```

```{r}
length(F1_DF_Clean$participantID[F1_DF_Clean$OVERALL_AnyMH=="No" & F1_DF_Clean$Higest_F_EPDS<11])
```


```{r}
length(N1_dHCP$participantID[N1_DF_Clean$OVERALL_AnyMH=="Yes" & N1_dHCP$Highest_N_EPDS>10])
```

```{r}
length(N1_dHCP$participantID[N1_DF_Clean$OVERALL_AnyMH=="Yes" & N1_dHCP$Highest_N_EPDS<11])
```

```{r}
length(N1_dHCP$participantID[N1_DF_Clean$OVERALL_AnyMH=="No" & N1_dHCP$Highest_N_EPDS>10])
```

```{r}
length(N1_dHCP$participantID[N1_DF_Clean$OVERALL_AnyMH=="No" & N1_dHCP$Highest_N_EPDS<11])
```






Same but for EPDS-3A
```{r}
length(Highest_EPDS3A_Fetal$participantID[Highest_EPDS3A_Fetal$ANY_ANX=="Yes" & Highest_EPDS3A_Fetal$HF_EPDS3A>3])
```

```{r}
length(Highest_EPDS3A_Fetal$participantID[Highest_EPDS3A_Fetal$ANY_ANX=="Yes" & Highest_EPDS3A_Fetal$HF_EPDS3A<4])
```

```{r}
length(Highest_EPDS3A_Fetal$participantID[Highest_EPDS3A_Fetal$ANY_ANX=="No" & Highest_EPDS3A_Fetal$HF_EPDS3A>3])
```

```{r}
length(Highest_EPDS3A_Fetal$participantID[Highest_EPDS3A_Fetal$ANY_ANX=="No" & Highest_EPDS3A_Fetal$HF_EPDS3A<4])
```


```{r}
length(Highest_EPDS3A_Neonatal$participantID[Highest_EPDS3A_Neonatal$ANY_ANX=="Yes" & Highest_EPDS3A_Neonatal$HN_EPDS3A>3])
```

```{r}
length(Highest_EPDS3A_Neonatal$participantID[Highest_EPDS3A_Neonatal$ANY_ANX=="Yes" & Highest_EPDS3A_Neonatal$HN_EPDS3A<4])
```

```{r}
length(Highest_EPDS3A_Neonatal$participantID[Highest_EPDS3A_Neonatal$ANY_ANX=="No" & Highest_EPDS3A_Neonatal$HN_EPDS3A>3])
```

```{r}
length(Highest_EPDS3A_Neonatal$participantID[Highest_EPDS3A_Neonatal$ANY_ANX=="No" & Highest_EPDS3A_Neonatal$HN_EPDS3A<4])
```






# REFERENCES FOR PACKAGES USED
Factor analysis was performed with 
```{r results='hide'}
citation(package = "nFactors")
citation(package="GPArotation")
citation(package="lavaan")
citation (package="MBESS")
```

Graphs were created with 
```{r}
citation(package="ggplot2")
citation(package="cowplot")
citation(package="harrypotter")
```

Data manipulation and calculation of effect sizes was performed with 
```{r results}
citation(package = "Hmisc")
citation(package = "plyr")
citation(package = "psych")
citation(package = "dplyr")
citation(package = "janitor")
citation(package = "rcompanion")
citation(package = "pastecs")
citation(package = "tidyr")
citation(package = "reshape2")
citation(package="effsize")
```






